---
title: "MYSTI Study – E-field x Behaviour Correlation"
subtitle: "HP-Head Field Strength vs Recollection Forgetting (TIS+Cue, TIS+Cue delayed)"
author: "Prince Okyere"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
    theme: flatly
    highlight: tango
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 8,
  fig.height = 5,
  dpi = 300
)
rm(list = ls())
```

Nature Neuroscience figure dimensions: 89mm per panel, 7pt font.

---

# 1. Setup

## 1.1 Load packages

```{r packages}
required_packages <- c("tidyverse", "readxl", "ggplot2",
                       "patchwork", "scales", "lme4",
                       "lmerTest", "emmeans", "svglite")

for (pkg in required_packages) {
  if (!requireNamespace(pkg, quietly = TRUE)) install.packages(pkg)
  library(pkg, character.only = TRUE)
}
cat("All packages loaded\n")
```

## 1.2 Paths and constants

```{r config}
# ==== EDIT FOR YOUR ENVIRONMENT ====
BASE_PATH       <- "/path/to/MYSTI"
BEHAVIOUR_FILE  <- "/path/to/MYSTI/FamRecFid_Tables/MYSTI_FamRecFid_V2_NAkept.xlsx"
# ====================================

efield_file <- file.path(BASE_PATH, "ALL_subjects_TI_metrics.csv")
out_dir     <- file.path(BASE_PATH, "derivatives", "EField_Behaviour")
dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)
cat("Output folder:", out_dir, "\n")

# Nature figure settings
fig_width_single <- 89    # mm - single column
fig_width_double <- 183   # mm - double column
fig_height_mm    <- 65    # mm
font_size        <- 10    # matches the behavioural analysis notebook's base_size
# font_family intentionally not set - relies on ggplot2's device default,
# consistent with the behavioural analysis notebook
```

## 1.3 Load E-field data (Left HP-Head, scaled x4)

Simulations were run at 0.25:0.75 mA; actual delivery was 1:3 mA.

```{r load_efield}
df_ef <- read.csv(efield_file)
df_ef <- df_ef[, !grepl("^Unnamed", colnames(df_ef))]
colnames(df_ef) <- c("Subject", "Region", "Strength", "Selectivity", "Collateral")

hp_head <- df_ef %>%
  filter(Region == "Left-HP_head") %>%
  distinct(Subject, .keep_all = TRUE) %>%
  mutate(HP_Head_Strength = Strength * 4) %>%
  rename(participant_id = Subject) %>%
  select(participant_id, HP_Head_Strength,
         HP_Head_Selectivity = Selectivity,
         HP_Head_Collateral  = Collateral)

cat(sprintf("HP-Head E-field: %d participants\n", nrow(hp_head)))
```

## 1.4 Load behaviour data

Recollection forgetting (V2), TIS+Cue conditions only.
`forgetting_pct = 100 - recollection_pct`.

```{r load_behaviour}
behav <- read_excel(BEHAVIOUR_FILE, sheet = "EEG_Correlation_Master")

behav_long <- bind_rows(
  behav %>%
    transmute(participant_id, condition = "TIS+Cue",
              forgetting_pct = 100 - V2_TISCue_recollection_pct),
  behav %>%
    transmute(participant_id, condition = "TIS+Cue delayed",
              forgetting_pct = 100 - V2_TISCue_delayed_recollection_pct)
)

merged <- inner_join(behav_long, hp_head, by = "participant_id") %>%
  mutate(
    participant_id = factor(participant_id),
    condition       = factor(condition, levels = c("TIS+Cue", "TIS+Cue delayed"))
  )

cat(sprintf("Merged: %d participants x %d conditions\n",
            n_distinct(merged$participant_id), nlevels(merged$condition)))
```

---

# 2. Correlation Analysis

LME collapsed across conditions (participant as random effect), plus a
per-condition simple regression (one observation per participant, so `lm`
not `lmer`) with Pearson correlation and BH-FDR correction.

```{r run_metric_helper}
run_metric <- function(data, predictor, label) {

  cat("\n", strrep("=", 55), "\n", sep = "")
  cat("METRIC:", label, "\n")
  cat(strrep("=", 55), "\n")

  data[[paste0(predictor, "_z")]] <- scale(data[[predictor]])[, 1]
  pred_z <- paste0(predictor, "_z")

  # LME A: collapsed across conditions
  m_all <- lmer(as.formula(paste0(
    "forgetting_pct ~ ", pred_z, " + condition + (1|participant_id)")),
    data = data, REML = FALSE)

  cat("\nLME A (collapsed): forgetting ~", label, "+ condition\n")
  print(summary(m_all)$coefficients)

  # LM per condition + Pearson correlation
  cat("\nLM per condition:\n")
  cor_table <- data.frame()

  for (cond in c("TIS+Cue", "TIS+Cue delayed")) {
    d_cond <- data %>% filter(condition == cond)
    m_cond <- lm(as.formula(paste0("forgetting_pct ~ ", pred_z)), data = d_cond)
    coef_row <- summary(m_cond)$coefficients[pred_z, ]

    cat(sprintf("  %-20s: beta=%.3f, SE=%.3f, t=%.3f, p=%.4f\n",
                cond, coef_row["Estimate"], coef_row["Std. Error"],
                coef_row["t value"], coef_row["Pr(>|t|)"]))

    x <- d_cond[[predictor]]
    y <- d_cond$forgetting_pct
    keep <- !is.na(x) & !is.na(y)
    r <- cor.test(x[keep], y[keep], method = "pearson")

    cor_table <- bind_rows(cor_table, data.frame(
      Metric    = label,
      Condition = cond,
      r_pearson = round(r$estimate, 3),
      p_pearson = round(r$p.value, 4),
      n         = sum(keep)
    ))
  }

  # BH-FDR across the conditions tested for this metric
  cor_table$p_fdr <- round(p.adjust(cor_table$p_pearson, method = "BH"), 4)
  cor_table$sig <- case_when(
    cor_table$p_fdr < 0.001 ~ "***",
    cor_table$p_fdr < 0.01  ~ "**",
    cor_table$p_fdr < 0.05  ~ "*",
    cor_table$p_fdr < 0.10  ~ "\u2020",
    TRUE                    ~ "ns"
  )

  print(cor_table)

  list(lme = m_all, cor_table = cor_table)
}

cat("Helper defined\n")
```

```{r run_head_strength}
results <- list()
results$head_str <- run_metric(merged, "HP_Head_Strength", "HP-Head Strength (V/m)")

write.csv(results$head_str$cor_table,
          file.path(out_dir, "HP_Head_Strength_correlations.csv"),
          row.names = FALSE)
```

---

# 3. Scatter Plots

No on-plot r/p/n annotation — those stats live in the CSV above only,
to keep the plots clean. Condition colours match `COL_COND` from the
behavioural analysis notebook, so colours are consistent across the
behavioural and E-field figures.

```{r fig_efield_behaviour, fig.width=6.4, fig.height=3.2}
condition_colors <- c(
  "TIS+Cue"         = "#9B8FD4",
  "TIS+Cue delayed" = "#4A90D9"
)

make_scatter <- function(data, predictor, cor_table, xlabel, cond) {

  d <- data %>% filter(condition == cond)

  ggplot(d, aes(x = .data[[predictor]], y = forgetting_pct)) +
    geom_smooth(method = "lm", se = TRUE,
                colour = condition_colors[[cond]],
                fill   = condition_colors[[cond]],
                alpha  = 0.15, linewidth = 0.8) +
    geom_point(size = 3, shape = 21,
               fill = condition_colors[[cond]],
               colour = "black", stroke = 0.5, alpha = 0.9) +
    scale_x_continuous(labels = label_number(accuracy = 0.01)) +
    labs(x = xlabel, y = "Forgetting (%)", title = cond) +
    theme_classic(base_size = font_size) +
    theme(
      plot.title  = element_text(size = font_size + 1, face = "bold", hjust = 0.5),
      axis.text   = element_text(size = font_size),
      axis.title  = element_text(size = font_size),
      axis.line   = element_line(linewidth = 0.3),
      axis.ticks  = element_line(linewidth = 0.3),
      plot.margin = margin(2, 2, 2, 2, "mm")
    )
}

cor_head_str <- results$head_str$cor_table

p1 <- make_scatter(merged, "HP_Head_Strength", cor_head_str,
                   "HP-Head Field Strength (V/m)", "TIS+Cue")
p2 <- make_scatter(merged, "HP_Head_Strength", cor_head_str,
                   "HP-Head Field Strength (V/m)", "TIS+Cue delayed")

combined <- (p1 | p2)
print(combined)

# Combined 2-panel figure, sized to match the behavioural notebook's
# combined-figure width
ggsave(file.path(out_dir, "fig_efield_behaviour.png"),
       combined, width = 6.4, height = 3.2, dpi = 600)
ggsave(file.path(out_dir, "fig_efield_behaviour.pdf"),
       combined, width = 6.4, height = 3.2, device = cairo_pdf)
ggsave(file.path(out_dir, "fig_efield_behaviour.svg"),
       combined, width = 6.4, height = 3.2, device = "svg")

# Individual panels, 3.2 x 3.2 in, matching the behavioural notebook's figures
ggsave(file.path(out_dir, "scatter_TISCue.png"),
       p1, width = 3.2, height = 3.2, dpi = 600)
ggsave(file.path(out_dir, "scatter_TISCue.pdf"),
       p1, width = 3.2, height = 3.2, device = cairo_pdf)
ggsave(file.path(out_dir, "scatter_TISCue.svg"),
       p1, width = 3.2, height = 3.2, device = "svg")

ggsave(file.path(out_dir, "scatter_TISCue_delayed.png"),
       p2, width = 3.2, height = 3.2, dpi = 600)
ggsave(file.path(out_dir, "scatter_TISCue_delayed.pdf"),
       p2, width = 3.2, height = 3.2, device = cairo_pdf)
ggsave(file.path(out_dir, "scatter_TISCue_delayed.svg"),
       p2, width = 3.2, height = 3.2, device = "svg")

cat("Saved combined (6.4 x 3.2 in) and individual (3.2 x 3.2 in) panels to:\n")
cat(out_dir, "\n")
```

---

# 4. Session Information

```{r session_info}
sessionInfo()
```
