---
title: "MYSTI Study – E-field Subregion Analysis"
subtitle: "Hippocampal Head vs Body vs Tail: Strength, Selectivity, Collateral"
author: "Prince Okyere"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
    theme: flatly
    highlight: tango
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 8,
  fig.height = 5,
  dpi = 300
)
rm(list = ls())
```

Nature Neuroscience figure dimensions: 183mm double column, 7pt font. LME
pairwise contrasts with FDR correction plus beeswarm dots.

---

# 1. Setup

## 1.1 Load packages

```{r packages}
required_packages <- c("tidyverse", "lme4", "lmerTest", "emmeans",
                       "ggplot2", "ggbeeswarm", "patchwork",
                       "ggsignif", "scales", "svglite")

for (pkg in required_packages) {
  if (!requireNamespace(pkg, quietly = TRUE)) install.packages(pkg)
  library(pkg, character.only = TRUE)
}
cat("All packages loaded\n")
```

## 1.2 Paths and constants

```{r config}
# ==== EDIT FOR YOUR ENVIRONMENT ====
BIDS_ROOT      <- "/path/to/BIDS"
EFIELD_DERIV   <- file.path(BIDS_ROOT, "derivatives", "efield")
# ====================================

out_dir <- file.path(BIDS_ROOT, "derivatives", "EField_Subregions")
dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)
cat("Output folder:", out_dir, "\n")

# Nature figure settings
fig_width_mm  <- 183   # double column
fig_height_mm <- 60    # adjust if brackets need more space
font_size     <- 10    # matches the behavioural analysis notebook's base_size
# font_family intentionally not set - relies on ggplot2's device default,
# consistent with the behavioural analysis notebook
```

## 1.3 Load data

```{r load_data}
df <- read.csv(file.path(EFIELD_DERIV, "desc-EField_metrics.csv"))
df <- df[, !grepl("^Unnamed", colnames(df))]
colnames(df) <- c("Subject", "Region", "Strength", "Selectivity", "Collateral")

# Scale strength by factor of 4 (simulation 0.25:0.75 mA -> actual 1:3 mA)
df$Strength <- ifelse(df$Region %in% c("Left-HP_head","Left-HP_body","Left-HP_tail"),
                      df$Strength * 4, df$Strength)

ROI <- c("Left-HP_head", "Left-HP_body", "Left-HP_tail")

roi_df <- df %>%
  filter(Region %in% ROI) %>%
  mutate(
    Region  = factor(Region,
                     levels = ROI,
                     labels = c("HP-Head", "HP-Body", "HP-Tail")),
    Subject = factor(Subject)
  )

cat("Subjects:", nlevels(roi_df$Subject), "\n")
print(table(roi_df$Region))
```

---

# 2. Descriptive Statistics

```{r descriptives}
desc_all <- map_dfr(c("Strength", "Selectivity", "Collateral"), function(metric) {
  roi_df %>%
    group_by(Region) %>%
    summarise(
      Metric = metric,
      n      = n(),
      Mean   = round(mean(.data[[metric]]),   2),
      SD     = round(sd(.data[[metric]]),     2),
      Median = round(median(.data[[metric]]), 2),
      Q25    = round(quantile(.data[[metric]], 0.25), 2),
      Q75    = round(quantile(.data[[metric]], 0.75), 2),
      .groups = "drop"
    )
})
print(desc_all)
write.csv(desc_all, file.path(out_dir, "descriptive_stats.csv"), row.names = FALSE)
```

---

# 3. LME and Pairwise Contrasts

```{r lme_contrasts}
lme_results <- list()

for (metric in c("Strength", "Selectivity", "Collateral")) {
  cat("\n===", metric, "===\n")

  formula <- as.formula(paste(metric, "~ Region + (1|Subject)"))
  m <- lmerTest::lmer(formula, data = roi_df, REML = FALSE)

  cat("LME:\n")
  print(anova(m))

  emm   <- emmeans(m, ~ Region)
  pairs <- as.data.frame(pairs(emm, adjust = "fdr"))
  cat("Pairwise contrasts (FDR):\n")
  print(pairs)

  lme_results[[metric]] <- list(model = m, emm = emm, pairs = pairs)
}

write.csv(
  bind_rows(lapply(names(lme_results), function(m) {
    cbind(Metric = m, lme_results[[m]]$pairs)
  })),
  file.path(out_dir, "lme_pairwise_contrasts.csv"),
  row.names = FALSE
)
```

---

# 4. Plots

## 4.1 Helper functions

```{r plot_helpers}
get_sig_pairs <- function(metric) {
  lme_results[[metric]]$pairs %>%
    filter(p.value < 0.05) %>%
    mutate(
      r1  = trimws(gsub("\\(|\\)", "", sub(" - .*", "", contrast))),
      r2  = trimws(gsub("\\(|\\)", "", sub(".* - ", "", contrast))),
      sig = case_when(
        p.value < 0.001 ~ "***",
        p.value < 0.01  ~ "**",
        TRUE            ~ "*"
      )
    ) %>%
    select(r1, r2, sig)
}

palette <- c(
  "HP-Head" = "#E76F51",
  "HP-Body" = "#2A9D8F",
  "HP-Tail" = "#A68A64"
)

y_labels <- c(
  Strength    = "Strength (V/m)",
  Selectivity = "Selectivity",
  Collateral  = "Collateral (%)"
)

make_barplot <- function(metric, data) {

  sum_df <- data %>%
    group_by(Region) %>%
    summarise(
      Mean = mean(.data[[metric]]),
      SEM  = sd(.data[[metric]]) / sqrt(n()),
      .groups = "drop"
    )

  sig_pairs   <- get_sig_pairs(metric)
  comparisons <- mapply(c, sig_pairs$r1, sig_pairs$r2, SIMPLIFY = FALSE)
  annotations <- sig_pairs$sig

  data_max <- max(sum_df$Mean + sum_df$SEM)
  step     <- data_max * 0.12
  y_steps  <- seq(
    data_max + step,
    data_max + step * max(length(comparisons), 1),
    by = step
  )
  y_limit <- ifelse(length(comparisons) > 0,
                    max(y_steps) * 1.1,
                    data_max * 1.25)

  ggplot(sum_df, aes(x = Region, y = Mean, fill = Region)) +
    geom_col(width = 0.65, colour = "black", linewidth = 0.3) +
    geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                  width = 0.15, linewidth = 0.3) +
    geom_beeswarm(
      data        = data,
      aes(x = Region, y = .data[[metric]]),
      size        = 0.8,
      alpha       = 0.70,
      cex         = 1.2,
      shape       = 21,
      fill        = "white",
      colour      = "black",
      stroke      = 0.3,
      inherit.aes = FALSE
    ) +
    { if (length(comparisons) > 0)
      ggsignif::geom_signif(
        comparisons = comparisons,
        annotations = annotations,
        y_position  = y_steps,
        tip_length  = 0.005,
        textsize    = 2.5,
        vjust       = 0.3,
        colour      = "black",
        size        = 0.3
      )
    } +
    scale_fill_manual(values = palette) +
    scale_y_continuous(
      labels = label_number(accuracy = 0.01),
      expand = expansion(mult = c(0.02, 0.02)),
      limits = c(0, y_limit)
    ) +
    labs(x = NULL, y = y_labels[[metric]]) +
    theme_classic(base_size = font_size) +
    theme(
      legend.position  = "none",
      axis.text.x      = element_text(size = font_size),
      axis.text.y      = element_text(size = font_size),
      axis.title.y     = element_text(size = font_size),
      axis.line        = element_line(linewidth = 0.3),
      axis.ticks       = element_line(linewidth = 0.3),
      plot.margin      = margin(2, 2, 2, 2, "mm")
    )
}

cat("Plot helpers defined\n")
```

## 4.2 Build and save figures

Panel sizes (3.2 x 3.2 in individual, 9.6 x 3.5 in combined) match the
behavioural analysis notebook's figures rather than the mm-based Nature
dimensions used elsewhere in this notebook, so exported SVGs open at a
consistent size across the whole figure set without needing to resize.

```{r fig_efield_subregions, fig.width=9.6, fig.height=3.5}
p1 <- make_barplot("Strength",    roi_df)
p2 <- make_barplot("Selectivity", roi_df)
p3 <- make_barplot("Collateral",  roi_df)

combined <- (p1 | p2 | p3) +
  plot_layout(widths = c(1, 1, 1))

print(combined)

# Save as TIFF at 600 dpi — Nature standard
ggsave(file.path(out_dir, "fig_efield_subregions.tiff"),
       combined, width = 9.6, height = 3.5, dpi = 600, device = "tiff")

# PDF for vector editing in Illustrator
ggsave(file.path(out_dir, "fig_efield_subregions.pdf"),
       combined, width = 9.6, height = 3.5, device = cairo_pdf)

# SVG, same size as the combined behavioural figures
ggsave(file.path(out_dir, "fig_efield_subregions.svg"),
       combined, width = 9.6, height = 3.5, device = "svg")

# Individual panels, same size as the single-panel behavioural figures
ggsave(file.path(out_dir, "bar_Strength.tiff"),
       p1, width = 3.2, height = 3.2, dpi = 600)
ggsave(file.path(out_dir, "bar_Strength.svg"),
       p1, width = 3.2, height = 3.2, device = "svg")

ggsave(file.path(out_dir, "bar_Selectivity.tiff"),
       p2, width = 3.2, height = 3.2, dpi = 600)
ggsave(file.path(out_dir, "bar_Selectivity.svg"),
       p2, width = 3.2, height = 3.2, device = "svg")

ggsave(file.path(out_dir, "bar_Collateral.tiff"),
       p3, width = 3.2, height = 3.2, dpi = 600)
ggsave(file.path(out_dir, "bar_Collateral.svg"),
       p3, width = 3.2, height = 3.2, device = "svg")

cat("Saved combined (9.6 x 3.5 in) and individual (3.2 x 3.2 in) panels to:\n")
cat(out_dir, "\n")
```

---

# 5. Session Information

```{r session_info}
sessionInfo()
```
