---
title: "MYSTI Study – E-field x Behaviour Correlation"
subtitle: "HP-Head Field Strength vs Recollection Forgetting (TIS+Cue, TIS+Cue delayed)"
author: "Prince Okyere"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
    theme: flatly
    highlight: tango
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Overview

This notebook tests whether individual differences in hippocampal head (HP-Head)
E-field **strength**, **selectivity**, and **collateral exposure** relate to
associative recall forgetting, separately for the **TIS+Cue** and
**TIS+Cue delayed** conditions.

For each E-field metric, two models are fitted:

1. **No-covariate model** — tests the raw relationship between the metric,
   condition, and forgetting.
2. **Covariate model** — repeats the same model including each participant's
   Cue-only forgetting rate as a covariate, to check whether any effect is
   specific to the field metric rather than a general trait-level tendency
   to forget more.

---

# Step 1 — Load packages

```{r packages}
required_packages <- c(
  "tidyverse", "readxl", "ggplot2", "patchwork", "scales",
  "lme4", "lmerTest", "emmeans", "svglite", "effectsize",
  "car", "interactions"
)

missing_packages <- required_packages[
  !sapply(required_packages, requireNamespace, quietly = TRUE)
]

if (length(missing_packages) > 0) {
  stop(
    "Missing packages: ", paste(missing_packages, collapse = ", "),
    "\nInstall with: install.packages(c(",
    paste0('"', missing_packages, '"', collapse = ", "), "))"
  )
}

invisible(lapply(required_packages, library, character.only = TRUE))
```

# Step 2 — Set paths and figure/colour conventions

```{r paths}
base        <- "C:/Users/po00240/OneDrive - University of Surrey/Desktop/Projects/MYSTI"
behav_v2    <- "C:/Users/po00240/OneDrive - University of Surrey/Desktop/Wake_behavior_data/figure3/FamRecFid_Tables/MYSTI_FamRecFid_V2_NAkept.xlsx"
efield_file <- file.path(base, "ALL_subjects_TI_metrics.csv")
out_dir     <- file.path(base, "stats_output", "EField_Behaviour")
dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)
```

```{r theme}
# Condition colours, used consistently across all figures in this project
condition_colors <- c(
  "TIS+Cue"         = "#BE83DC",  # purple
  "TIS+Cue delayed" = "#2E97EE"   # blue
)

# Plain, no-gridline theme matching the rest of the manuscript figures
theme_nature <- theme_minimal(base_size = 10) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line  = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_line(color = "black", linewidth = 0.4),
    legend.position = "top"
  )
```

# Step 3 — Load and merge data

```{r load-data}
# E-field metrics: Left HP-Head only, strength scaled x4
# (simulation 0.25:0.75 mA -> actual 1:3 mA delivery)
df_ef <- read.csv(efield_file)
df_ef <- df_ef[, !grepl("^Unnamed", colnames(df_ef))]
colnames(df_ef) <- c("Subject", "Region", "Strength", "Selectivity", "Collateral")

hp_head <- df_ef %>%
  filter(Region == "Left-HP_head") %>%
  distinct(Subject, .keep_all = TRUE) %>%
  mutate(HP_Head_Strength = Strength * 4) %>%
  rename(participant_id = Subject) %>%
  dplyr::select(participant_id, HP_Head_Strength,
                HP_Head_Selectivity = Selectivity,
                HP_Head_Collateral  = Collateral)

# Behaviour: forgetting_pct = 100 - recollection_pct
behav <- read_excel(behav_v2, sheet = "EEG_Correlation_Master")

behav_cue <- behav %>%
  transmute(participant_id, CueOnlyForgetting = 100 - V2_Cue_recollection_pct)

behav_long <- bind_rows(
  behav %>% transmute(participant_id, condition = "TIS+Cue",
                       forgetting_pct = 100 - V2_TISCue_recollection_pct),
  behav %>% transmute(participant_id, condition = "TIS+Cue delayed",
                       forgetting_pct = 100 - V2_TISCue_delayed_recollection_pct)
) %>%
  left_join(behav_cue, by = "participant_id")

merged <- inner_join(behav_long, hp_head, by = "participant_id") %>%
  mutate(
    participant_id = factor(participant_id),
    condition = factor(condition, levels = c("TIS+Cue", "TIS+Cue delayed"))
  )

cat(sprintf("Merged: %d participants x %d conditions\n",
            n_distinct(merged$participant_id), nlevels(merged$condition)))
```

# Step 4 — No-covariate models

Formula: `forgetting_pct ~ condition * metric + (1|participant_id)`

```{r no-cov-models}
m1_raw <- lmer(forgetting_pct ~ condition * HP_Head_Strength    + (1|participant_id), data = merged)
m2_raw <- lmer(forgetting_pct ~ condition * HP_Head_Selectivity + (1|participant_id), data = merged)
m3_raw <- lmer(forgetting_pct ~ condition * HP_Head_Collateral  + (1|participant_id), data = merged)
```

## Kenward-Roger F-tests (no covariate)

```{r no-cov-anova}
car::Anova(m1_raw, test.statistic = "F")   # Strength
car::Anova(m2_raw, test.statistic = "F")   # Selectivity
car::Anova(m3_raw, test.statistic = "F")   # Collateral
```

# Step 5 — Covariate models

Formula: `forgetting_pct ~ condition * metric + CueOnlyForgetting + (1|participant_id)`

Repeats each model above, adding each participant's Cue-only forgetting rate
as a covariate, to test whether effects are specific to the field metric
rather than a general tendency to forget more.

```{r cov-models}
m1 <- lmer(forgetting_pct ~ condition * HP_Head_Strength    + CueOnlyForgetting + (1|participant_id), data = merged)
m2 <- lmer(forgetting_pct ~ condition * HP_Head_Selectivity + CueOnlyForgetting + (1|participant_id), data = merged)
m3 <- lmer(forgetting_pct ~ condition * HP_Head_Collateral  + CueOnlyForgetting + (1|participant_id), data = merged)
```

## Kenward-Roger F-tests (with covariate)

```{r cov-anova}
car::Anova(m1, test.statistic = "F")   # Strength
car::Anova(m2, test.statistic = "F")   # Selectivity
car::Anova(m3, test.statistic = "F")   # Collateral
```

# Step 6 — Simple slopes for the Selectivity interaction

Where a condition x metric interaction is present, `emtrends` gives the
condition-specific slope (Satterthwaite degrees of freedom).

```{r emtrends}
trends <- emtrends(m2, ~ condition, var = "HP_Head_Selectivity")
summary(trends, infer = c(TRUE, TRUE))

# Test whether the two slopes differ (= the interaction term, reparameterised)
emtrends(m2, pairwise ~ condition, var = "HP_Head_Selectivity", adjust = "none")
```

# Step 7 — Figures

```{r figure-function}
run_efield_plot <- function(model, predictor, label = predictor) {
  plot_obj <- interact_plot(
    model, pred = !!sym(predictor), modx = condition,
    interval = TRUE, int.type = "confidence", plot.points = TRUE,
    colors = c(condition_colors["TIS+Cue"], condition_colors["TIS+Cue delayed"]),
    line.thickness = 2.0,
    x.label = gsub("_", " ", predictor), y.label = "Forgetting (%)", legend.main = ""
  ) + theme_nature

  safe_label <- gsub("[^A-Za-z0-9_-]", "_", label)
  ggsave(file.path(out_dir, paste0(safe_label, "_interaction_plot.svg")),
         plot_obj, width = 70, height = 60, units = "mm")
  ggsave(file.path(out_dir, paste0(safe_label, "_interaction_plot.png")),
         plot_obj, width = 70, height = 60, units = "mm", dpi = 600)
  print(plot_obj)
}
```

```{r figures, fig.width=4, fig.height=3.5}
run_efield_plot(m1, "HP_Head_Strength",    label = "m1_HP_Head_Strength_covariate")
run_efield_plot(m2, "HP_Head_Selectivity", label = "m2_HP_Head_Selectivity_covariate")
run_efield_plot(m3, "HP_Head_Collateral",  label = "m3_HP_Head_Collateral_covariate")
```

# Summary of results

