---
title: "MYSTI Study – Behavioural Analysis"
subtitle: "Effect of TIS on Sleep-Dependent Memory Consolidation"
author: "Prince Okyere"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: show
    theme: flatly
    highlight: tango
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 8,
  fig.height = 5,
  dpi = 300
)
rm(list = ls())
```

---

# 1. Setup

## 1.1 Load packages

```{r packages}
required_packages <- c(
  "readxl", "writexl", "dplyr", "tidyr",
  "lme4", "lmerTest", "emmeans", "car",
  "ggplot2", "scales", "patchwork",
  "knitr", "kableExtra", "ordinal",
  "svglite",  # needed for ggsave(..., device = "svg")
  "DHARMa"    # simulated-residual diagnostics for the GLMMs/LMM below
)
new_pkg <- required_packages[!(required_packages %in% installed.packages()[,"Package"])]
if (length(new_pkg)) install.packages(new_pkg, dependencies = TRUE)
invisible(lapply(required_packages, library, character.only = TRUE))
cat("All packages loaded\n")
```

## 1.2 Paths and constants

```{r config}
# ==== EDIT FOR YOUR ENVIRONMENT ====
BASE_PATH    <- "/path/to/MYSTI/Wake_behavior_data"
# ====================================

PRE_FILE     <- file.path(BASE_PATH, "Participants_pre_data_transcribed_corrected.xlsx")
POST_FILE    <- file.path(BASE_PATH, "Participants_post_data_transcribed_corrected.xlsx")
FIG_DIR      <- file.path(BASE_PATH, "Figures")
TABLE_DIR    <- file.path(BASE_PATH, "Tables")
SUPP_FIG_DIR <- file.path(BASE_PATH, "Supplementary", "Figures2")
SUPP_TAB_DIR <- file.path(BASE_PATH, "Supplementary", "Tables2")

dir.create(FIG_DIR,      showWarnings = FALSE, recursive = TRUE)
dir.create(TABLE_DIR,    showWarnings = FALSE, recursive = TRUE)
dir.create(SUPP_FIG_DIR, showWarnings = FALSE, recursive = TRUE)
dir.create(SUPP_TAB_DIR, showWarnings = FALSE, recursive = TRUE)

COND_LABELS <- c("1" = "TIS+Cue", "2" = "TIS+Cue delayed",
                 "3" = "Cue",     "4" = "Non-Cue")
COND_LEVELS <- c("TIS+Cue", "TIS+Cue delayed", "Cue", "Non-Cue")

COL_COND <- c(
  "TIS+Cue"         = "#9B8FD4",
  "TIS+Cue delayed" = "#4A90D9",
  "Cue"             = "#1BC4C4",
  "Non-Cue"         = "#34495E"
)

numify <- function(x) suppressWarnings(as.numeric(as.character(x)))

# NOTE: bracket spacing tightened (pp_max + 1 + 2.5*n instead of + 3 + 5*n)
# per Valeria's comment - brackets were taking up too much vertical space
# and sitting too far from the data.
#
# NOTE: tier assignment is now overlap-aware. Previously every bracket got
# the next sequential tier regardless of whether it actually crossed any
# other bracket's x-range - this pushed non-overlapping pairs (e.g.
# TIS+Cue vs TIS+Cue delayed, and Cue vs Non-Cue, which don't share any
# x-position) to different heights for no reason. Now a bracket only moves
# up a tier if its x-range actually overlaps a bracket already placed at
# the current tier.
assign_bracket_tiers <- function(df) {
  df <- df %>% arrange(abs(x2 - x1))
  tiers <- integer(nrow(df))
  tier_ranges <- list()  # tier_ranges[[tier]] = list of c(xmin,xmax) already placed

  # Safe accessor: list()[[idx]] errors when idx exceeds current length
  # (unlike vectors, which return NA) - this avoids that error.
  safe_get <- function(lst, idx) if (idx <= length(lst)) lst[[idx]] else NULL

  for (i in seq_len(nrow(df))) {
    xr <- sort(c(df$x1[i], df$x2[i]))
    tier <- 1
    repeat {
      existing <- safe_get(tier_ranges, tier)
      overlaps <- FALSE
      if (!is.null(existing)) {
        for (rng in existing) {
          if (xr[1] < rng[2] && rng[1] < xr[2]) { overlaps <- TRUE; break }
        }
      }
      if (!overlaps) break
      tier <- tier + 1
    }
    tiers[i] <- tier
    tier_ranges[[tier]] <- c(safe_get(tier_ranges, tier), list(xr))
  }
  df$tier <- tiers
  df
}

get_sig_pairs <- function(pair_df, cond_levels, pp_max) {
  as.data.frame(summary(pair_df)) %>%
    filter(p.value < .10) %>%
    mutate(
      contrast = as.character(contrast),
      g1  = gsub("[()]", "", trimws(sapply(strsplit(contrast, " / "), `[`, 1))),
      g2  = gsub("[()]", "", trimws(sapply(strsplit(contrast, " / "), `[`, 2))),
      x1  = match(g1, cond_levels),
      x2  = match(g2, cond_levels),
      sig = ifelse(p.value < .001, "***",
                   ifelse(p.value < .01,  "**",
                          ifelse(p.value < .05, "*", "\u2020")))
    ) %>%
    filter(!is.na(x1), !is.na(x2)) %>%
    assign_bracket_tiers() %>%
    mutate(y_bar = pp_max + 2 + 4.5 * tier)
}

get_sig_pairs_gated <- function(pair_df, cond_levels, pp_max, omnibus_p) {
  if (omnibus_p >= .05) return(data.frame())
  get_sig_pairs(pair_df, cond_levels, pp_max)
}

# DHARMa simulated-residual diagnostics, run after every GLMM/LMM fit below.
# Reports dispersion, uniformity (KS), and outlier tests, plus the standard
# QQ / residual-vs-predicted plot. Note: DHARMa does not support `clmm`
# (ordinal package) objects, so the CLMM fidelity model in Section 7b.1 is
# not run through this helper - see the note there.
check_glmm_assumptions <- function(model, label) {
  cat(sprintf("\n%s\n", strrep("=", 60)))
  cat(sprintf("DHARMa diagnostics: %s\n", label))
  cat(sprintf("%s\n\n", strrep("=", 60)))

  sim_res <- simulateResiduals(model, plot = FALSE)
  plot(sim_res)

  disp_test <- testDispersion(sim_res, plot = FALSE)
  unif_test <- testUniformity(sim_res, plot = FALSE)
  outl_test <- testOutliers(sim_res, plot = FALSE)

  cat(sprintf("Dispersion test:  stat = %.3f, p = %.4f  [%s]\n",
              disp_test$statistic, disp_test$p.value,
              ifelse(disp_test$p.value > .05, "OK", "CHECK")))
  cat(sprintf("Uniformity (KS):  D    = %.3f, p = %.4f  [%s]\n",
              unif_test$statistic, unif_test$p.value,
              ifelse(unif_test$p.value > .05, "OK", "CHECK")))
  cat(sprintf("Outlier test:     p = %.4f  [%s]\n",
              outl_test$p.value,
              ifelse(outl_test$p.value > .05, "OK", "CHECK")))

  invisible(sim_res)
}

cat("Configuration complete\n")
```

## 1.3 Load raw data

```{r load_data}
pre_raw <- read_excel(PRE_FILE, sheet = "Sheet1") %>%
  filter(!is.na(words), trimws(words) != "") %>%
  mutate(
    word_acc            = as.integer(numify(word_selection_Accuracy)),
    img_acc             = as.integer(numify(Images_Selection_Accuracy)),
    scale               = as.integer(numify(`scale manual`)),
    Confidence          = numify(Confidence_Rating),
    Word_reaction_time  = numify(Word_reaction_time),
    Image_reaction_time = numify(Image_reaction_time),
    Condition           = as.factor(Condition),
    sub                 = as.factor(participant_id),
    stim_type           = as.factor(Images_Faces_Object_),
    block               = as.integer(numify(Block)),
    session             = "Pre"
  )

post_raw <- read_excel(POST_FILE, sheet = "Sheet1") %>%
  filter(!is.na(words), trimws(words) != "") %>%
  mutate(
    word_acc            = as.integer(numify(word_selection_Accuracy)),
    img_acc             = as.integer(numify(Images_Selection_Accuracy)),
    scale               = as.integer(numify(`scale manual`)),
    Confidence          = numify(Confidence_Rating),
    Word_reaction_time  = numify(Word_reaction_time),
    Image_reaction_time = numify(Image_reaction_time),
    Condition           = as.factor(Condition),
    sub                 = as.factor(participant_id),
    stim_type           = as.factor(Images_Faces_Object_),
    block               = as.integer(numify(Block)),
    session             = "Post"
  )

cat(sprintf("PRE  rows: %d | Participants: %d\n", nrow(pre_raw), n_distinct(pre_raw$sub)))
cat(sprintf("POST rows: %d | Participants: %d\n", nrow(post_raw), n_distinct(post_raw$sub)))
```

## 1.4 Build matched dataset

```{r matched_data}
pre_correct <- pre_raw %>%
  filter(Corr_resp_Old_New_ == "Old", !is.na(Condition),
         word_acc == 1, img_acc == 1) %>%
  select(sub, words, Condition, stim_type, block,
         pre_word = word_acc, pre_img = img_acc,
         pre_scale = scale, pre_conf = Confidence)

post_items <- post_raw %>%
  filter(Corr_resp_Old_New_ == "Old", !is.na(Condition)) %>%
  select(sub, words, Condition,
         post_word = word_acc, post_img = img_acc,
         post_scale = scale, post_conf = Confidence,
         post_selection = Selection_Old_New_,
         post_face_obj  = Images_Faces_Object_,
         post_img_selection = Selection_Images_)

matched <- inner_join(pre_correct, post_items,
                      by = c("sub", "words", "Condition")) %>%
  mutate(Condition_f = factor(COND_LABELS[as.character(Condition)],
                              levels = COND_LEVELS))

cat(sprintf("Matched items: %d\n", nrow(matched)))
matched %>% count(Condition_f) %>% print()
```

## 1.5 Sanity check

```{r sanity_check}
pre_counts  <- pre_correct %>%
  mutate(Condition_f = factor(COND_LABELS[as.character(Condition)], levels = COND_LEVELS)) %>%
  count(Condition_f, name = "Pre_N")
post_counts <- post_items %>%
  mutate(Condition_f = factor(COND_LABELS[as.character(Condition)], levels = COND_LEVELS)) %>%
  count(Condition_f, name = "Post_N")
matched_counts <- matched %>% count(Condition_f, name = "Matched_N")

check <- pre_counts %>%
  left_join(post_counts, by = "Condition_f") %>%
  left_join(matched_counts, by = "Condition_f") %>%
  mutate(Pre_vs_Post = Pre_N - Post_N, Pre_vs_Matched = Pre_N - Matched_N)
print(check)

if (any(check$Pre_vs_Matched != 0)) {
  cat("\nWARNING: items lost in join.\n")
} else {
  cat("\nOK: no items lost.\n")
}
```

## 1.6 Compute outcomes

```{r outcomes}
matched <- matched %>%
  mutate(
    fam_correct    = as.integer(post_selection == "Old"),
    fam_forgetting = as.integer(post_selection != "Old")
  )

matched_rec <- matched %>%
  filter(!is.na(post_img_selection)) %>%
  mutate(
    rec_correct    = as.integer(post_selection == "Old" & post_face_obj == post_img_selection),
    rec_forgetting = as.integer(!(post_selection == "Old" & post_face_obj == post_img_selection))
  )

matched_fid <- matched %>%
  filter(!is.na(post_img_selection), !is.na(post_scale)) %>%
  mutate(
    fid_correct    = as.integer(post_selection == "Old" &
                                post_face_obj == post_img_selection & post_scale >= 1),
    fid_forgetting = as.integer(!(post_selection == "Old" &
                                  post_face_obj == post_img_selection & post_scale >= 1))
  )

cat(sprintf("Familiarity: %d | Recollection: %d | Fidelity: %d\n",
            nrow(matched), nrow(matched_rec), nrow(matched_fid)))
```

---

# 2. Overall Memory Change

```{r overall_change}
acc_wide <- inner_join(
  pre_raw %>% filter(Corr_resp_Old_New_ == "Old") %>%
    mutate(word_acc_filled = ifelse(is.na(word_acc), 0L, word_acc),
           img_acc_filled  = ifelse(is.na(img_acc),  0L, img_acc)) %>%
    group_by(sub) %>%
    summarise(Pre = mean(word_acc_filled == 1 & img_acc_filled == 1) * 100, .groups = "drop"),
  post_raw %>% filter(Corr_resp_Old_New_ == "Old") %>%
    mutate(word_acc_filled = ifelse(is.na(word_acc), 0L, word_acc),
           img_acc_filled  = ifelse(is.na(img_acc),  0L, img_acc)) %>%
    group_by(sub) %>%
    summarise(Post = mean(word_acc_filled == 1 & img_acc_filled == 1) * 100, .groups = "drop"),
  by = "sub")

t_res   <- t.test(acc_wide$Post, acc_wide$Pre, paired = TRUE)
cohen_d <- (mean(acc_wide$Pre) - mean(acc_wide$Post)) / sd(acc_wide$Pre - acc_wide$Post)

cat(sprintf("Pre:  %.1f%% (SD %.1f%%)\n", mean(acc_wide$Pre), sd(acc_wide$Pre)))
cat(sprintf("Post: %.1f%% (SD %.1f%%)\n", mean(acc_wide$Post), sd(acc_wide$Post)))
cat(sprintf("t(%d) = %.2f, p = %.4f, d = %.2f\n",
            t_res$parameter, t_res$statistic, t_res$p.value, cohen_d))
```

---

# 3. Face vs Object Memory

```{r face_object}
both_sess <- bind_rows(
  pre_raw  %>% filter(Corr_resp_Old_New_ == "Old") %>%
               mutate(session = "Pre",  Confidence_Rating = as.character(Confidence_Rating)),
  post_raw %>% filter(Corr_resp_Old_New_ == "Old") %>%
               mutate(session = "Post", Confidence_Rating = as.character(Confidence_Rating))
) %>%
  mutate(
    word_acc_filled = ifelse(is.na(word_acc), 0L, word_acc),
    img_acc_filled  = ifelse(is.na(img_acc),  0L, img_acc),
    correct   = as.integer(word_acc_filled == 1 & img_acc_filled == 1),
    session   = factor(session, levels = c("Pre", "Post")),
    stim_type = factor(Images_Faces_Object_)
  )

m_cat <- glmer(correct ~ stim_type * session + (1 | sub),
               data = both_sess, family = binomial,
               control = glmerControl(optimizer = "bobyqa"))
cat("=== Face vs Object ===\n")
print(Anova(m_cat, type = "II"))

emm_cat <- emmeans(m_cat, ~ stim_type | session, type = "response")
print(emm_cat)
```

```{r diag_m_cat, fig.width=8, fig.height=4}
check_glmm_assumptions(m_cat, "Face vs Object Memory (m_cat)")
```

---

# 4. TMR Efficacy (Cue vs Non-Cue)

```{r tmr_efficacy}
df_tmr <- matched_rec %>%
  filter(Condition_f %in% c("Cue", "Non-Cue")) %>%
  mutate(Condition_f = droplevels(Condition_f))

m_tmr <- glmer(rec_forgetting ~ Condition_f + (1 | sub),
               data = df_tmr, family = binomial,
               control = glmerControl(optimizer = "bobyqa"))

cat("=== TMR Efficacy ===\n")
tmr_anova <- Anova(m_tmr, type = "II")
print(tmr_anova)

emm_tmr  <- emmeans(m_tmr, ~ Condition_f, type = "response")
pair_tmr <- contrast(emm_tmr, method = "pairwise", adjust = "none")
print(summary(pair_tmr))
```

```{r diag_m_tmr, fig.width=8, fig.height=4}
check_glmm_assumptions(m_tmr, "TMR Efficacy (m_tmr)")
```

---

# 5. Familiarity (Word Recognition)

```{r familiarity_glmm}
m_fam <- glmer(fam_forgetting ~ Condition_f + (1 | sub),
               data = matched, family = binomial,
               control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

cat("=== Familiarity GLMM ===\n")
fam_anova <- Anova(m_fam, type = "II")
print(fam_anova)

emm_fam  <- emmeans(m_fam, ~ Condition_f, type = "response")
pair_fam <- contrast(emm_fam, method = "pairwise", adjust = "none")
print(emm_fam)
print(summary(pair_fam))

pair_fam_logit <- contrast(emmeans(m_fam, ~ Condition_f),
                            method = "pairwise", adjust = "none")
print(summary(pair_fam_logit))
```

```{r diag_m_fam, fig.width=8, fig.height=4}
check_glmm_assumptions(m_fam, "Familiarity (m_fam)")
```

```{r fig_familiarity}
emm_fam_df <- as.data.frame(emm_fam) %>%
  mutate(rate_pct = prob * 100, lo_pct = asymp.LCL * 100, hi_pct = asymp.UCL * 100)

pp_familiarity <- matched %>%
  group_by(sub, Condition_f) %>%
  summarise(rate = mean(fam_forgetting, na.rm = TRUE) * 100, .groups = "drop")

sig_fam <- get_sig_pairs_gated(pair_fam, COND_LEVELS,
                               max(pp_familiarity$rate, na.rm = TRUE),
                               fam_anova$`Pr(>Chisq)`[1])

p_familiarity <- ggplot() +
  geom_col(data = emm_fam_df, aes(x = Condition_f, y = rate_pct, fill = Condition_f),
           width = 0.7, colour = NA) +
  geom_errorbar(data = emm_fam_df,
                aes(x = Condition_f, ymin = lo_pct, ymax = hi_pct),
                width = 0.15, linewidth = 0.8, colour = "black") +
  geom_line(data = pp_familiarity,
            aes(x = as.numeric(Condition_f), y = rate, group = sub),
            colour = "grey65", linewidth = 0.45, alpha = 0.65) +
  # Data point size reduced per Derk-Jan's comment (size 2.2 -> 1.4, stroke 0.6 -> 0.5)
  geom_point(data = pp_familiarity,
             aes(x = Condition_f, y = rate, fill = Condition_f),
             shape = 21, size = 1.4, stroke = 0.5, colour = "black", alpha = 0.85,
             position = position_jitter(width = 0.06, seed = 123, height = 0)) +
  { if (nrow(sig_fam) > 0) list(
      geom_segment(data = sig_fam, aes(x=x1,xend=x2,y=y_bar,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data = sig_fam, aes(x=x1,xend=x1,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data = sig_fam, aes(x=x2,xend=x2,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_text(data=sig_fam, aes(x=(x1+x2)/2,y=y_bar+2,label=sig),
                size=5, inherit.aes=FALSE)
  )} +
  scale_fill_manual(values = COL_COND) +
  scale_y_continuous(labels = percent_format(accuracy=1,scale=1),
                     expand = expansion(mult=c(0,0.2)), limits=c(0,NA)) +
  labs(x = NULL, y = "Word Recognition Forgetting (%)") +
  theme_classic(base_size = 10) +
  theme(legend.position="none",
        axis.line=element_line(linewidth=0.8,colour="black"),
        axis.text.x=element_text(size=10,colour="black",angle=30,hjust=1),
        axis.text.y=element_text(size=10,colour="black"),
        axis.title=element_text(size=10,colour="black"),
        plot.margin=margin(10,10,15,10)) +
  coord_cartesian(clip="off")

print(p_familiarity)
ggsave(file.path(FIG_DIR, "Fig_4_Familiarity.png"), p_familiarity, width=3.2, height=3.2, dpi=600)
ggsave(file.path(FIG_DIR, "Fig_4_Familiarity.pdf"), p_familiarity, width=3.2, height=3.2, device=cairo_pdf)
ggsave(file.path(FIG_DIR, "Fig_4_Familiarity.svg"), p_familiarity, width=3.2, height=3.2, device="svg")
cat("Familiarity figure saved.\n")
```

---

# 6. Recollection (Primary Outcome)

```{r recollection_glmm}
m_rec <- glmer(rec_forgetting ~ Condition_f + (1 | sub),
               data = matched_rec, family = binomial,
               control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

cat("=== Recollection GLMM ===\n")
rec_anova <- Anova(m_rec, type = "II")
print(rec_anova)

emm_rec  <- emmeans(m_rec, ~ Condition_f, type = "response")
pair_rec <- contrast(emm_rec, method = "pairwise", adjust = "none")
print(emm_rec)
print(summary(pair_rec))

pair_rec_logit <- contrast(emmeans(m_rec, ~ Condition_f),
                            method = "pairwise", adjust = "none")
print(summary(pair_rec_logit))

rec_rates <- matched_rec %>%
  group_by(Condition_f) %>%
  summarise(N=n(), Correct_pct=round(mean(rec_correct)*100,1),
            Forgetting_pct=round(mean(rec_forgetting)*100,1),
            SE=round(sd(rec_forgetting)/sqrt(n())*100,1), .groups="drop")
kable(rec_rates, caption="Recollection by condition") %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"))
```

```{r diag_m_rec, fig.width=8, fig.height=4}
check_glmm_assumptions(m_rec, "Recollection - PRIMARY OUTCOME (m_rec)")
```

```{r fig_recollection}
emm_rec_df <- as.data.frame(emm_rec) %>%
  mutate(rate_pct=prob*100, lo_pct=asymp.LCL*100, hi_pct=asymp.UCL*100)

pp_recollection <- matched_rec %>%
  group_by(sub, Condition_f) %>%
  summarise(rate=mean(rec_forgetting,na.rm=TRUE)*100, .groups="drop")

sig_rec <- get_sig_pairs_gated(pair_rec, COND_LEVELS,
                               max(pp_recollection$rate,na.rm=TRUE),
                               rec_anova$`Pr(>Chisq)`[1])

# Compute how much headroom the stacked brackets actually need, so the
# visible panel range comfortably fits all of them (previously,
# scale_y_continuous(limits=...) silently DELETED any bracket whose y_bar
# exceeded 50, which is why only the lowest bracket survived).
n_sig_rec   <- nrow(sig_rec)
bracket_top <- if (n_sig_rec > 0) max(sig_rec$y_bar) + 3 else max(pp_recollection$rate, na.rm=TRUE) + 5

p_recollection <- ggplot() +
  geom_col(data=emm_rec_df, aes(x=Condition_f,y=rate_pct,fill=Condition_f),
           width=0.7, colour=NA) +
  geom_errorbar(data=emm_rec_df, aes(x=Condition_f,ymin=lo_pct,ymax=hi_pct),
                width=0.15, linewidth=0.8, colour="black") +
  geom_line(data=pp_recollection, aes(x=as.numeric(Condition_f),y=rate,group=sub),
            colour="grey65", linewidth=0.45, alpha=0.65) +
  # Data point size reduced per Derk-Jan's comment (size 2.2 -> 1.4, stroke 0.6 -> 0.5)
  geom_point(data=pp_recollection, aes(x=Condition_f,y=rate,fill=Condition_f),
             shape=21, size=1.4, stroke=0.5, colour="black", alpha=0.85,
             position=position_jitter(width=0.06,seed=123,height=0)) +
  { if (nrow(sig_rec) > 0) list(
      geom_segment(data=sig_rec, aes(x=x1,xend=x2,y=y_bar,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_rec, aes(x=x1,xend=x1,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_rec, aes(x=x2,xend=x2,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_text(data=sig_rec, aes(x=(x1+x2)/2,y=y_bar+2,label=sig),
                size=5, inherit.aes=FALSE)
  )} +
  scale_fill_manual(values=COL_COND) +
  # Per Valeria's comment: axis LABELS still stop at 50% (visual impression
  # she asked for), but the actual panel range (via coord_cartesian below)
  # extends far enough to fit all significance brackets without deleting them.
  scale_y_continuous(labels=percent_format(accuracy=1,scale=1),
                     breaks=seq(0,50,10)) +
  coord_cartesian(ylim = c(0, bracket_top), clip = "off") +
  labs(x=NULL, y="Associative Recall Forgetting (%)") +
  theme_classic(base_size=10) +
  theme(legend.position="none",
        axis.line=element_line(linewidth=0.8,colour="black"),
        axis.text.x=element_text(size=10,colour="black",angle=30,hjust=1),
        axis.text.y=element_text(size=10,colour="black"),
        axis.title=element_text(size=10,colour="black"),
        plot.margin=margin(10,10,15,10))

print(p_recollection)
ggsave(file.path(FIG_DIR,"Fig_5_Recollection_Primary.png"), p_recollection, width=3.2, height=3.2, dpi=600)
ggsave(file.path(FIG_DIR,"Fig_5_Recollection_Primary.pdf"), p_recollection, width=3.2, height=3.2, device=cairo_pdf)
ggsave(file.path(FIG_DIR,"Fig_5_Recollection_Primary.svg"), p_recollection, width=3.2, height=3.2, device="svg")
cat("Recollection figure saved.\n")
```

---

# 7. Fidelity — Binary (original)

```{r fidelity_glmm}
m_fid <- glmer(fid_forgetting ~ Condition_f + (1 | sub),
               data = matched_fid, family = binomial,
               control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

cat("=== Fidelity GLMM ===\n")
fid_anova <- Anova(m_fid, type = "II")
print(fid_anova)

emm_fid  <- emmeans(m_fid, ~ Condition_f, type = "response")
pair_fid <- contrast(emm_fid, method = "pairwise", adjust = "none")
print(emm_fid)
print(summary(pair_fid))

pair_fid_logit <- contrast(emmeans(m_fid, ~ Condition_f),
                            method = "pairwise", adjust = "none")
print(summary(pair_fid_logit))
```

```{r diag_m_fid, fig.width=8, fig.height=4}
check_glmm_assumptions(m_fid, "Fidelity - binary (m_fid)")
```

```{r fig_fidelity}
emm_fid_df <- as.data.frame(emm_fid) %>%
  mutate(rate_pct=prob*100, lo_pct=asymp.LCL*100, hi_pct=asymp.UCL*100)

pp_fidelity <- matched_fid %>%
  group_by(sub, Condition_f) %>%
  summarise(rate=mean(fid_forgetting,na.rm=TRUE)*100, .groups="drop")

p_fidelity <- ggplot() +
  geom_col(data=emm_fid_df, aes(x=Condition_f,y=rate_pct,fill=Condition_f),
           width=0.7, colour=NA) +
  geom_errorbar(data=emm_fid_df, aes(x=Condition_f,ymin=lo_pct,ymax=hi_pct),
                width=0.15, linewidth=0.8, colour="black") +
  geom_line(data=pp_fidelity, aes(x=as.numeric(Condition_f),y=rate,group=sub),
            colour="grey65", linewidth=0.45, alpha=0.65) +
  # Data point size reduced per Derk-Jan's comment (size 2.2 -> 1.4, stroke 0.6 -> 0.5)
  geom_point(data=pp_fidelity, aes(x=Condition_f,y=rate,fill=Condition_f),
             shape=21, size=1.4, stroke=0.5, colour="black", alpha=0.85,
             position=position_jitter(width=0.06,seed=123,height=0)) +
  scale_fill_manual(values=COL_COND) +
  scale_y_continuous(labels=percent_format(accuracy=1,scale=1),
                     expand=expansion(mult=c(0,0.2)), limits=c(0,NA)) +
  labs(x=NULL, y="Fidelity Forgetting (%)") +
  theme_classic(base_size=8) +
  theme(legend.position="none",
        axis.line=element_line(linewidth=0.8,colour="black"),
        axis.text.x=element_text(size=8,colour="black",angle=30,hjust=1),
        axis.text.y=element_text(size=8,colour="black"),
        axis.title=element_text(size=8,colour="black"),
        plot.margin=margin(10,10,15,10)) +
  coord_cartesian(clip="off")

print(p_fidelity)
ggsave(file.path(FIG_DIR,"Fig_6_Fidelity.png"), p_fidelity, width=3.2, height=3.5, dpi=600)
ggsave(file.path(FIG_DIR,"Fig_6_Fidelity.pdf"), p_fidelity, width=3.2, height=3.5, device=cairo_pdf)
ggsave(file.path(FIG_DIR,"Fig_6_Fidelity.svg"), p_fidelity, width=3.2, height=3.5, device="svg")
cat("Fidelity figure saved.\n")
```

---

# 7b. Fidelity — Ordinal & Recoded Analyses

## 7b.1 Cumulative-Link Mixed Model (CLMM) on raw 0–3 scores

```{r fidelity_clmm}
matched_ord <- matched %>%
  filter(!is.na(post_img_selection), !is.na(post_scale)) %>%
  mutate(fidelity_score = factor(post_scale, levels = 0:3, ordered = TRUE))

cat(sprintf("Items for ordinal analysis: %d\n", nrow(matched_ord)))

m_clmm <- clmm(fidelity_score ~ Condition_f + (1 | sub),
               data = matched_ord, link = "logit", threshold = "flexible")

m_clmm_null <- clmm(fidelity_score ~ 1 + (1 | sub),
                    data = matched_ord, link = "logit", threshold = "flexible")

cat("\n=== CLMM Summary ===\n")
print(summary(m_clmm))

cat("\n=== Likelihood Ratio Test ===\n")
lrt <- anova(m_clmm_null, m_clmm)
print(lrt)

cat("\n=== Pairwise comparisons ===\n")
emm_ord  <- emmeans(m_clmm, ~ Condition_f, mode = "linear.predictor")
pair_ord <- contrast(emm_ord, method = "pairwise", adjust = "none")
print(summary(pair_ord))
```

```{r diag_m_clmm_note, results='asis'}
cat("**Note on assumption checks for m_clmm:** DHARMa's `simulateResiduals()` ",
    "does not support `clmm` objects from the `ordinal` package (only lm, ",
    "glm, lme4, glmmTMB, GLMMadaptive, and a few others are supported), so ",
    "the same diagnostic battery used for the binomial GLMMs above cannot ",
    "be run on this model directly. As a partial check, the recoded binary ",
    "version of this outcome (Section 7b.3, `m_fid2`) covers the same data ",
    "with a `glmer` model that DOES get full DHARMa diagnostics below - ",
    "convergence and consistency between `m_clmm` and `m_fid2` is one way ",
    "to gain some assurance the ordinal model's conclusions aren't an ",
    "artefact of a violated assumption.\n")
```

## 7b.2 Stacked bar plot — ordinal score distribution

```{r fig_fidelity_ordinal}
prop_df <- matched_ord %>%
  count(Condition_f, fidelity_score) %>%
  group_by(Condition_f) %>%
  mutate(prop = n / sum(n) * 100) %>%
  ungroup() %>%
  mutate(score_label = factor(fidelity_score,
                              levels = c(3, 2, 1, 0),
                              labels = c("3 — Accurate detail",
                                         "2 — Correct category",
                                         "1 — Related/confused",
                                         "0 — No recall")))

score_colours <- c(
  "3 — Accurate detail"  = "#2C7BB6",
  "2 — Correct category" = "#ABD9E9",
  "1 — Related/confused" = "#FDAE61",
  "0 — No recall"        = "#D7191C"
)

p_ord <- ggplot(prop_df, aes(x = Condition_f, y = prop, fill = score_label)) +
  geom_col(width = 0.7, colour = "white", linewidth = 0.3) +
  scale_fill_manual(values = score_colours, name = "Fidelity score") +
  scale_y_continuous(labels = percent_format(accuracy=1,scale=1),
                     expand = expansion(mult=c(0,0.02))) +
  labs(x = NULL, y = "Proportion of items (%)") +
  theme_classic(base_size = 8) +
  theme(legend.position="right",
        legend.title=element_text(size=8,face="bold"),
        legend.text=element_text(size=7),
        axis.line=element_line(linewidth=0.4,colour="black"),
        axis.text.x=element_text(size=8,colour="black",angle=30,hjust=1),
        axis.text.y=element_text(size=8,colour="black"),
        axis.title=element_text(size=8,colour="black"),
        plot.margin=margin(10,10,15,10))

print(p_ord)
ggsave(file.path(FIG_DIR,"Fig_6b_Fidelity_OrdinalStacked.png"), p_ord, width=3.5, height=3.2, dpi=600)
ggsave(file.path(FIG_DIR,"Fig_6b_Fidelity_OrdinalStacked.pdf"), p_ord, width=3.5, height=3.2, device=cairo_pdf)
ggsave(file.path(FIG_DIR,"Fig_6b_Fidelity_OrdinalStacked.svg"), p_ord, width=3.5, height=3.2, device="svg")
cat("Ordinal stacked bar saved.\n")
```

## 7b.3 Recoded binary: 0+1 = forgetting, 2+3 = retained

```{r fidelity_recoded}
matched_fid2 <- matched %>%
  filter(!is.na(post_scale)) %>%
  mutate(
    fid2_retained   = as.integer(post_scale >= 2),
    fid2_forgetting = as.integer(post_scale < 2)
  )

cat(sprintf("Fidelity recoded items: %d\n", nrow(matched_fid2)))
matched_fid2 %>%
  group_by(Condition_f) %>%
  summarise(N=n(),
            Retained_pct=round(mean(fid2_retained)*100,1),
            Forgetting_pct=round(mean(fid2_forgetting)*100,1), .groups="drop") %>%
  print()

m_fid2 <- glmer(fid2_forgetting ~ Condition_f + (1 | sub),
                data = matched_fid2, family = binomial,
                control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

cat("\n=== Fidelity Recoded GLMM ===\n")
fid2_anova <- Anova(m_fid2, type = "II")
print(fid2_anova)

emm_fid2  <- emmeans(m_fid2, ~ Condition_f, type = "response")
pair_fid2 <- contrast(emm_fid2, method = "pairwise", adjust = "none")
print(emm_fid2)
print(summary(pair_fid2))

pair_fid2_logit <- contrast(emmeans(m_fid2, ~ Condition_f),
                             method = "pairwise", adjust = "none")
print(summary(pair_fid2_logit))
```

```{r diag_m_fid2, fig.width=8, fig.height=4}
check_glmm_assumptions(m_fid2, "Fidelity - recoded binary (m_fid2)")
```

```{r fig_fidelity_recoded}
emm_fid2_df <- as.data.frame(emm_fid2) %>%
  mutate(rate_pct=prob*100, lo_pct=asymp.LCL*100, hi_pct=asymp.UCL*100)

pp_fid2 <- matched_fid2 %>%
  group_by(sub, Condition_f) %>%
  summarise(rate=mean(fid2_forgetting,na.rm=TRUE)*100, .groups="drop")

sig_fid2 <- get_sig_pairs_gated(pair_fid2, COND_LEVELS,
                                max(pp_fid2$rate,na.rm=TRUE),
                                fid2_anova$`Pr(>Chisq)`[1])

p_fid2 <- ggplot() +
  geom_col(data=emm_fid2_df, aes(x=Condition_f,y=rate_pct,fill=Condition_f),
           width=0.7, colour=NA) +
  geom_errorbar(data=emm_fid2_df, aes(x=Condition_f,ymin=lo_pct,ymax=hi_pct),
                width=0.15, linewidth=0.8, colour="black") +
  geom_line(data=pp_fid2, aes(x=as.numeric(Condition_f),y=rate,group=sub),
            colour="grey65", linewidth=0.45, alpha=0.65) +
  # Data point size reduced per Derk-Jan's comment (size 2.2 -> 1.4, stroke 0.6 -> 0.5)
  geom_point(data=pp_fid2, aes(x=Condition_f,y=rate,fill=Condition_f),
             shape=21, size=1.4, stroke=0.5, colour="black", alpha=0.85,
             position=position_jitter(width=0.06,seed=123,height=0)) +
  { if (nrow(sig_fid2) > 0) list(
      geom_segment(data=sig_fid2, aes(x=x1,xend=x2,y=y_bar,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_fid2, aes(x=x1,xend=x1,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_fid2, aes(x=x2,xend=x2,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_text(data=sig_fid2, aes(x=(x1+x2)/2,y=y_bar+2,label=sig),
                size=5, inherit.aes=FALSE)
  )} +
  scale_fill_manual(values=COL_COND) +
  scale_y_continuous(labels=percent_format(accuracy=1,scale=1),
                     expand=expansion(mult=c(0,0.2)), limits=c(0,NA)) +
  labs(x=NULL, y="Fidelity Forgetting (%)") +
  theme_classic(base_size=8) +
  theme(legend.position="none",
        axis.line=element_line(linewidth=0.8,colour="black"),
        axis.text.x=element_text(size=8,colour="black",angle=30,hjust=1),
        axis.text.y=element_text(size=8,colour="black"),
        axis.title=element_text(size=8,colour="black"),
        plot.margin=margin(10,10,15,10)) +
  coord_cartesian(clip="off")

print(p_fid2)
ggsave(file.path(FIG_DIR,"Fig_6c_Fidelity_Recoded.png"), p_fid2, width=3.2, height=3.5, dpi=600)
ggsave(file.path(FIG_DIR,"Fig_6c_Fidelity_Recoded.pdf"), p_fid2, width=3.2, height=3.5, device=cairo_pdf)
ggsave(file.path(FIG_DIR,"Fig_6c_Fidelity_Recoded.svg"), p_fid2, width=3.2, height=3.5, device="svg")
cat("Fidelity recoded figure saved.\n")
```

## 7b.4 Forgetting index (pre − post score)

```{r fidelity_index}
matched_fid_idx <- matched %>%
  filter(!is.na(pre_scale), pre_scale >= 1, !is.na(post_scale)) %>%
  mutate(fid_forgetting_index = pre_scale - post_scale)

cat("=== Fidelity Forgetting Index (pre - post) ===\n")
matched_fid_idx %>%
  group_by(Condition_f) %>%
  summarise(N    = n(),
            Mean = round(mean(fid_forgetting_index, na.rm = TRUE), 3),
            SD   = round(sd(fid_forgetting_index,   na.rm = TRUE), 3),
            .groups = "drop") %>%
  print()

# Aggregate to participant level first
pp_fid_idx <- matched_fid_idx %>%
  group_by(sub, Condition_f) %>%
  summarise(mean_idx = mean(fid_forgetting_index, na.rm = TRUE), .groups = "drop")

# LME on participant-level means
m_fid_idx <- lmer(mean_idx ~ Condition_f + (1 | sub),
                  data = pp_fid_idx)

cat("\n=== Fidelity Index LME — ANOVA (participant level) ===\n")
print(anova(m_fid_idx))

emm_idx  <- emmeans(m_fid_idx, ~ Condition_f)
pair_idx <- contrast(emm_idx, method = "pairwise", adjust = "none")
print(emm_idx)
print(summary(pair_idx))
```

```{r diag_m_fid_idx, fig.width=8, fig.height=4}
check_glmm_assumptions(m_fid_idx, "Fidelity Forgetting Index (m_fid_idx, LMM)")
```

```{r fig_fidelity_index}
# Define pp_idx FIRST
pp_idx <- matched_fid_idx %>%
  group_by(sub, Condition_f) %>%
  summarise(rate=mean(fid_forgetting_index,na.rm=TRUE), .groups="drop")

# Significance bars - spacing increased to prevent brackets/asterisks overlapping
sig_idx <- as.data.frame(summary(pair_idx)) %>%
  filter(p.value < .06) %>%
  mutate(
    contrast = as.character(contrast),
    g1  = gsub("[()]", "", trimws(sapply(strsplit(contrast, " - "), `[`, 1))),
    g2  = gsub("[()]", "", trimws(sapply(strsplit(contrast, " - "), `[`, 2))),
    x1  = match(g1, COND_LEVELS),
    x2  = match(g2, COND_LEVELS),
    sig = ifelse(p.value < .001, "***",
                 ifelse(p.value < .01,  "**",
                        ifelse(p.value < .05, "*", "\u2020")))
  ) %>%
  filter(!is.na(x1), !is.na(x2)) %>%
  arrange(abs(x2 - x1)) %>%
  mutate(y_bar = max(pp_idx$rate, na.rm = TRUE) + 0.15 + 0.35 * seq_len(n()))

emm_idx_df <- as.data.frame(emm_idx) %>%
  rename(rate_pct=emmean, lo_pct=lower.CL, hi_pct=upper.CL)

p_fid_idx <- ggplot() +
  geom_col(data=emm_idx_df, aes(x=Condition_f,y=rate_pct,fill=Condition_f),
           width=0.7, colour=NA) +
  geom_errorbar(data=emm_idx_df, aes(x=Condition_f,ymin=lo_pct,ymax=hi_pct),
                width=0.15, linewidth=0.8, colour="black") +
  geom_line(data=pp_idx, aes(x=as.numeric(Condition_f),y=rate,group=sub),
            colour="grey65", linewidth=0.45, alpha=0.65) +
  # Data point size reduced per Derk-Jan's comment (size 2.2 -> 1.4, stroke 0.6 -> 0.5)
  geom_point(data=pp_idx, aes(x=Condition_f,y=rate,fill=Condition_f),
             shape=21, size=1.4, stroke=0.5, colour="black", alpha=0.85,
             position=position_jitter(width=0.06,seed=123,height=0)) +
  geom_hline(yintercept=0, linetype="dashed", colour="grey40", linewidth=0.4) +
  { if (nrow(sig_idx) > 0) list(
      geom_segment(data=sig_idx,
                   aes(x=x1, xend=x2, y=y_bar, yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_idx,
                   aes(x=x1, xend=x1, y=y_bar-0.10, yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_idx,
                   aes(x=x2, xend=x2, y=y_bar-0.10, yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_text(data=sig_idx,
                aes(x=(x1+x2)/2, y=y_bar+0.10, label=sig),
                size=5, inherit.aes=FALSE)
  )} +
  scale_fill_manual(values=COL_COND) +
  scale_y_continuous(expand=expansion(mult=c(0.1,0.22))) +
  labs(x=NULL, y="Fidelity Forgetting Index\n(pre \u2212 post score)") +
  theme_classic(base_size=10) +
  theme(legend.position="none",
        axis.line=element_line(linewidth=0.8,colour="black"),
        axis.text.x=element_text(size=10,colour="black",angle=30,hjust=1),
        axis.text.y=element_text(size=10,colour="black"),
        axis.title=element_text(size=10,colour="black"),
        plot.margin=margin(10,10,15,10)) +
  coord_cartesian(clip="off")

print(p_fid_idx)
ggsave(file.path(FIG_DIR,"Fig_6d_Fidelity_Index.png"), p_fid_idx, width=3.2, height=3.2, dpi=600)
ggsave(file.path(FIG_DIR,"Fig_6d_Fidelity_Index.pdf"), p_fid_idx, width=3.2, height=3.2, device=cairo_pdf)
ggsave(file.path(FIG_DIR,"Fig_6d_Fidelity_Index.svg"), p_fid_idx, width=3.2, height=3.2, device="svg")
cat("Fidelity index figure saved.\n")
```

---

# 8. Combined Main Figure

```{r fig_combined_main}
p_main <- (p_recollection | p_familiarity | p_fidelity) +
  plot_annotation(tag_levels = "A")
print(p_main)
ggsave(file.path(FIG_DIR,"Fig_MAIN_Combined.png"), p_main, width=9.6, height=3.5, dpi=600)
ggsave(file.path(FIG_DIR,"Fig_MAIN_Combined.pdf"), p_main, width=9.6, height=3.5, device=cairo_pdf)
ggsave(file.path(FIG_DIR,"Fig_MAIN_Combined.svg"), p_main, width=9.6, height=3.5, device="svg")
cat("Combined figure saved.\n")
```

---

# 9. Recollection by Stimulus Category

```{r catcond_interaction}
m_cat_cond <- glmer(rec_forgetting ~ Condition_f * stim_type + (1 | sub),
                    data=matched_rec, family=binomial,
                    control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
cat("=== Condition x Category ===\n")
print(Anova(m_cat_cond, type="II"))
```

```{r diag_m_cat_cond, fig.width=8, fig.height=4}
check_glmm_assumptions(m_cat_cond, "Condition x Category interaction (m_cat_cond)")
```

```{r faces_objects}
matched_faces   <- matched_rec %>% filter(stim_type == "Face")
matched_objects <- matched_rec %>% filter(stim_type == "Object")

m_face <- glmer(rec_forgetting ~ Condition_f + (1 | sub), data=matched_faces,
                family=binomial, control=glmerControl(optimizer="bobyqa"))
cat("=== Faces ===\n"); print(Anova(m_face, type="II"))
print(summary(contrast(emmeans(m_face,~Condition_f), method="pairwise", adjust="none")))

m_obj <- glmer(rec_forgetting ~ Condition_f + (1 | sub), data=matched_objects,
               family=binomial, control=glmerControl(optimizer="bobyqa"))
cat("=== Objects ===\n"); print(Anova(m_obj, type="II"))
print(summary(contrast(emmeans(m_obj,~Condition_f), method="pairwise", adjust="none")))
```

```{r diag_m_face_obj, fig.width=8, fig.height=4}
check_glmm_assumptions(m_face, "Recollection - Faces only (m_face)")
check_glmm_assumptions(m_obj,  "Recollection - Objects only (m_obj)")
```

---

# 10. Supplementary

## S1. Block-level analysis

```{r supp_block}
pre_block <- pre_raw %>%
  filter(Corr_resp_Old_New_ == "Old") %>%
  mutate(word_acc_filled=ifelse(is.na(word_acc),0L,word_acc),
         img_acc_filled=ifelse(is.na(img_acc),0L,img_acc),
         correct=as.integer(word_acc_filled==1 & img_acc_filled==1),
         block=as.factor(block)) %>%
  filter(!is.na(block))

m_block <- glmer(correct ~ block + (1|sub), data=pre_block, family=binomial,
                 control=glmerControl(optimizer="bobyqa"))
cat("=== Block ===\n"); print(Anova(m_block, type="II"))
```

```{r diag_m_block, fig.width=8, fig.height=4}
check_glmm_assumptions(m_block, "Pre-nap block-level accuracy (m_block)")
```

## S2. False alarm rates

```{r supp_far}
far_df <- post_raw %>%
  filter(Corr_resp_Old_New_ == "New") %>%
  mutate(false_alarm=as.integer(Selection_Old_New_ == "Old")) %>%
  group_by(sub) %>%
  summarise(far=mean(false_alarm,na.rm=TRUE)*100, .groups="drop")

cat(sprintf("False alarm rate: Mean = %.1f%%  SD = %.1f%%\n",
            mean(far_df$far), sd(far_df$far)))
```

---

# 11. Export Tables

```{r export}
writexl::write_xlsx(
  list(
    Familiarity_rates  = matched %>%
      group_by(Condition_f) %>%
      summarise(N=n(), Correct_pct=round(mean(fam_correct)*100,1),
                Forgetting_pct=round(mean(fam_forgetting)*100,1),
                SE=round(sd(fam_forgetting)/sqrt(n())*100,1), .groups="drop"),
    Recollection_rates = rec_rates,
    Fidelity_rates     = matched_fid %>%
      group_by(Condition_f) %>%
      summarise(N=n(), Correct_pct=round(mean(fid_correct)*100,1),
                Forgetting_pct=round(mean(fid_forgetting)*100,1),
                SE=round(sd(fid_forgetting)/sqrt(n())*100,1), .groups="drop"),
    Fam_pairwise_OR    = as.data.frame(summary(pair_fam)),
    Fam_pairwise_zp    = as.data.frame(summary(pair_fam_logit)),
    Rec_pairwise_OR    = as.data.frame(summary(pair_rec)),
    Rec_pairwise_zp    = as.data.frame(summary(pair_rec_logit)),
    Fid_pairwise_OR    = as.data.frame(summary(pair_fid)),
    Fid_pairwise_zp    = as.data.frame(summary(pair_fid_logit)),
    Fid2_pairwise_OR   = as.data.frame(summary(pair_fid2)),
    Fid2_pairwise_zp   = as.data.frame(summary(pair_fid2_logit)),
    Fid_Index_pairwise = as.data.frame(summary(pair_idx)),
    TMR_pairwise       = as.data.frame(summary(pair_tmr)),
    False_alarm_rates  = far_df,
    PrePost_accuracy   = acc_wide
  ),
  path = file.path(TABLE_DIR, "MYSTI_Behavioural_Statistical_Results.xlsx")
)
cat(sprintf("Tables saved to: %s\n", TABLE_DIR))
```

---

# 12. Results Summary

```{r summary}
cat("══════════════════════════════════════════════════════════\n")
cat("RESULTS SUMMARY — BEHAVIOURAL ANALYSIS\n")
cat("══════════════════════════════════════════════════════════\n\n")

cat(sprintf("Overall pre vs post: t(%d) = %.2f, p = %.4f, d = %.2f\n\n",
            t_res$parameter, t_res$statistic, t_res$p.value, cohen_d))
cat(sprintf("TMR efficacy: chi2(%d) = %.2f, p = %.4f\n\n",
            tmr_anova$Df, tmr_anova$Chisq, tmr_anova$`Pr(>Chisq)`))
cat(sprintf("Familiarity: chi2(%d) = %.2f, p = %.4f\n\n",
            fam_anova$Df, fam_anova$Chisq, fam_anova$`Pr(>Chisq)`))
cat(sprintf("Recollection: chi2(%d) = %.2f, p = %.4f\n\n",
            rec_anova$Df, rec_anova$Chisq, rec_anova$`Pr(>Chisq)`))
cat(sprintf("Fidelity (binary): chi2(%d) = %.2f, p = %.4f\n\n",
            fid_anova$Df, fid_anova$Chisq, fid_anova$`Pr(>Chisq)`))
cat(sprintf("Fidelity (recoded 0+1 vs 2+3): chi2(%d) = %.2f, p = %.4f\n\n",
            fid2_anova$Df, fid2_anova$Chisq, fid2_anova$`Pr(>Chisq)`))
cat(sprintf("Fidelity CLMM (ordinal 0-3): LRT chi2(3) = %.2f, p = %.4f\n\n",
            lrt[2,"LR.stat"], lrt[2,"Pr(>Chisq)"]))
cat("══════════════════════════════════════════════════════════\n")
```

---

# 13. Session Information

```{r session_info}
sessionInfo()
```
