---
title: "MYSTI Study – Behavioural Analysis"
subtitle: "Effect of TIS on Sleep-Dependent Memory Consolidation"
author: "Prince Okyere"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: show
    theme: flatly
    highlight: tango
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 8,
  fig.height = 5,
  dpi = 300
)
rm(list = ls())
```

---

# 1. Setup

## 1.1 Load packages

```{r packages}
required_packages <- c(
  "readxl", "writexl", "dplyr", "tidyr",
  "lme4", "lmerTest", "emmeans", "car",
  "ggplot2", "scales", "patchwork",
  "knitr", "kableExtra",
  "svglite",  # needed for ggsave(..., device = "svg")
  "DHARMa"    # simulated-residual diagnostics for the GLMMs/LMM below
)
new_pkg <- required_packages[!(required_packages %in% installed.packages()[,"Package"])]
if (length(new_pkg)) install.packages(new_pkg, dependencies = TRUE)
invisible(lapply(required_packages, library, character.only = TRUE))
cat("All packages loaded\n")
```

## 1.2 Paths and constants

```{r config}
# ==== EDIT FOR YOUR ENVIRONMENT ====
BASE_PATH    <- "E:/BIDS/derivatives/behaviour"
# ====================================

PRE_FILE     <- file.path(BASE_PATH, "desc-preNapBehaviour_trialdata.xlsx")
POST_FILE    <- file.path(BASE_PATH, "desc-postNapBehaviour_trialdata.xlsx")
FIG_DIR      <- file.path(BASE_PATH, "Figures")
TABLE_DIR    <- file.path(BASE_PATH, "Tables")
SUPP_FIG_DIR <- file.path(BASE_PATH, "Supplementary", "Figures2")
SUPP_TAB_DIR <- file.path(BASE_PATH, "Supplementary", "Tables2")

dir.create(FIG_DIR,      showWarnings = FALSE, recursive = TRUE)
dir.create(TABLE_DIR,    showWarnings = FALSE, recursive = TRUE)
dir.create(SUPP_FIG_DIR, showWarnings = FALSE, recursive = TRUE)
dir.create(SUPP_TAB_DIR, showWarnings = FALSE, recursive = TRUE)

COND_LABELS <- c("1" = "TIS+Cue", "2" = "TIS+Cue delayed",
                 "3" = "Cue",     "4" = "Non-Cue")
COND_LEVELS <- c("TIS+Cue", "TIS+Cue delayed", "Cue", "Non-Cue")

COL_COND <- c(
  "TIS+Cue"         = "#9B8FD4",
  "TIS+Cue delayed" = "#4A90D9",
  "Cue"             = "#1BC4C4",
  "Non-Cue"         = "#34495E"
)

numify <- function(x) suppressWarnings(as.numeric(as.character(x)))


assign_bracket_tiers <- function(df) {
  df <- df %>% arrange(abs(x2 - x1))
  tiers <- integer(nrow(df))
  tier_ranges <- list()  # 


  safe_get <- function(lst, idx) if (idx <= length(lst)) lst[[idx]] else NULL

  for (i in seq_len(nrow(df))) {
    xr <- sort(c(df$x1[i], df$x2[i]))
    tier <- 1
    repeat {
      existing <- safe_get(tier_ranges, tier)
      overlaps <- FALSE
      if (!is.null(existing)) {
        for (rng in existing) {
          if (xr[1] < rng[2] && rng[1] < xr[2]) { overlaps <- TRUE; break }
        }
      }
      if (!overlaps) break
      tier <- tier + 1
    }
    tiers[i] <- tier
    tier_ranges[[tier]] <- c(safe_get(tier_ranges, tier), list(xr))
  }
  df$tier <- tiers
  df
}

get_sig_pairs <- function(pair_df, cond_levels, pp_max) {
  as.data.frame(summary(pair_df)) %>%
    filter(p.value < .10) %>%
    mutate(
      contrast = as.character(contrast),
      g1  = gsub("[()]", "", trimws(sapply(strsplit(contrast, " / "), `[`, 1))),
      g2  = gsub("[()]", "", trimws(sapply(strsplit(contrast, " / "), `[`, 2))),
      x1  = match(g1, cond_levels),
      x2  = match(g2, cond_levels),
      sig = ifelse(p.value < .001, "***",
                   ifelse(p.value < .01,  "**",
                          ifelse(p.value < .05, "*", "\u2020")))
    ) %>%
    filter(!is.na(x1), !is.na(x2)) %>%
    assign_bracket_tiers() %>%
    mutate(y_bar = pp_max + 2 + 4.5 * tier)
}

get_sig_pairs_gated <- function(pair_df, cond_levels, pp_max, omnibus_p) {
  if (omnibus_p >= .05) return(data.frame())
  get_sig_pairs(pair_df, cond_levels, pp_max)
}

# DHARMa simulated-residual diagnostics, run after every GLMM/LMM fit below.
# Reports dispersion, uniformity (KS), and outlier tests, plus the standard
# QQ / residual-vs-predicted plot. 

check_glmm_assumptions <- function(model, label) {
  cat(sprintf("\n%s\n", strrep("=", 60)))
  cat(sprintf("DHARMa diagnostics: %s\n", label))
  cat(sprintf("%s\n\n", strrep("=", 60)))

  sim_res <- simulateResiduals(model, plot = FALSE)
  plot(sim_res)

  disp_test <- testDispersion(sim_res, plot = FALSE)
  unif_test <- testUniformity(sim_res, plot = FALSE)
  outl_test <- testOutliers(sim_res, plot = FALSE)

  cat(sprintf("Dispersion test:  stat = %.3f, p = %.4f  [%s]\n",
              disp_test$statistic, disp_test$p.value,
              ifelse(disp_test$p.value > .05, "OK", "CHECK")))
  cat(sprintf("Uniformity (KS):  D    = %.3f, p = %.4f  [%s]\n",
              unif_test$statistic, unif_test$p.value,
              ifelse(unif_test$p.value > .05, "OK", "CHECK")))
  cat(sprintf("Outlier test:     p = %.4f  [%s]\n",
              outl_test$p.value,
              ifelse(outl_test$p.value > .05, "OK", "CHECK")))

  invisible(sim_res)
}

cat("Configuration complete\n")
```

## 1.3 Load raw data

```{r load_data}
pre_raw <- read_excel(PRE_FILE, sheet = "Sheet1") %>%
  filter(!is.na(words), trimws(words) != "") %>%
  mutate(
    word_acc            = as.integer(numify(word_selection_Accuracy)),
    img_acc             = as.integer(numify(Images_Selection_Accuracy)),
    scale               = as.integer(numify(`scale manual`)),
    Confidence          = numify(Confidence_Rating),
    Word_reaction_time  = numify(Word_reaction_time),
    Image_reaction_time = numify(Image_reaction_time),
    Condition           = as.factor(Condition),
    sub                 = as.factor(participant_id),
    stim_type           = as.factor(Images_Faces_Object_),
    block               = as.integer(numify(Block)),
    session             = "Pre"
  )

post_raw <- read_excel(POST_FILE, sheet = "Sheet1") %>%
  filter(!is.na(words), trimws(words) != "") %>%
  mutate(
    word_acc            = as.integer(numify(word_selection_Accuracy)),
    img_acc             = as.integer(numify(Images_Selection_Accuracy)),
    scale               = as.integer(numify(`scale manual`)),
    Confidence          = numify(Confidence_Rating),
    Word_reaction_time  = numify(Word_reaction_time),
    Image_reaction_time = numify(Image_reaction_time),
    Condition           = as.factor(Condition),
    sub                 = as.factor(participant_id),
    stim_type           = as.factor(Images_Faces_Object_),
    block               = as.integer(numify(Block)),
    session             = "Post"
  )

cat(sprintf("PRE  rows: %d | Participants: %d\n", nrow(pre_raw), n_distinct(pre_raw$sub)))
cat(sprintf("POST rows: %d | Participants: %d\n", nrow(post_raw), n_distinct(post_raw$sub)))
```

## 1.4 Build matched dataset

```{r matched_data}
pre_correct <- pre_raw %>%
  filter(Corr_resp_Old_New_ == "Old", !is.na(Condition),
         word_acc == 1, img_acc == 1) %>%
  select(sub, words, Condition, stim_type, block,
         pre_word = word_acc, pre_img = img_acc,
         pre_scale = scale, pre_conf = Confidence)

post_items <- post_raw %>%
  filter(Corr_resp_Old_New_ == "Old", !is.na(Condition)) %>%
  select(sub, words, Condition,
         post_word = word_acc, post_img = img_acc,
         post_scale = scale, post_conf = Confidence,
         post_selection = Selection_Old_New_,
         post_face_obj  = Images_Faces_Object_,
         post_img_selection = Selection_Images_)

matched <- inner_join(pre_correct, post_items,
                      by = c("sub", "words", "Condition")) %>%
  mutate(Condition_f = factor(COND_LABELS[as.character(Condition)],
                              levels = COND_LEVELS))

cat(sprintf("Matched items: %d\n", nrow(matched)))
matched %>% count(Condition_f) %>% print()
```

## 1.5 Sanity check

```{r sanity_check}
pre_counts  <- pre_correct %>%
  mutate(Condition_f = factor(COND_LABELS[as.character(Condition)], levels = COND_LEVELS)) %>%
  count(Condition_f, name = "Pre_N")
post_counts <- post_items %>%
  mutate(Condition_f = factor(COND_LABELS[as.character(Condition)], levels = COND_LEVELS)) %>%
  count(Condition_f, name = "Post_N")
matched_counts <- matched %>% count(Condition_f, name = "Matched_N")

check <- pre_counts %>%
  left_join(post_counts, by = "Condition_f") %>%
  left_join(matched_counts, by = "Condition_f") %>%
  mutate(Pre_vs_Post = Pre_N - Post_N, Pre_vs_Matched = Pre_N - Matched_N)
print(check)

if (any(check$Pre_vs_Matched != 0)) {
  cat("\nWARNING: items lost in join.\n")
} else {
  cat("\nOK: no items lost.\n")
}
```

## 1.6 Compute outcomes

```{r outcomes}
matched <- matched %>%
  mutate(
    fam_correct    = as.integer(post_selection == "Old"),
    fam_forgetting = as.integer(post_selection != "Old")
  )

matched_rec <- matched %>%
  filter(!is.na(post_img_selection)) %>%
  mutate(
    rec_correct    = as.integer(post_selection == "Old" & post_face_obj == post_img_selection),
    rec_forgetting = as.integer(!(post_selection == "Old" & post_face_obj == post_img_selection))
  )

matched_fid <- matched %>%
  filter(!is.na(post_img_selection), !is.na(post_scale)) %>%
  mutate(
    fid_correct    = as.integer(post_selection == "Old" &
                                post_face_obj == post_img_selection & post_scale >= 1),
    fid_forgetting = as.integer(!(post_selection == "Old" &
                                  post_face_obj == post_img_selection & post_scale >= 1))
  )

cat(sprintf("Familiarity: %d | Recollection: %d | Fidelity: %d\n",
            nrow(matched), nrow(matched_rec), nrow(matched_fid)))
```

---

# 2. Overall Memory Change

```{r overall_change}
acc_wide <- inner_join(
  pre_raw %>% filter(Corr_resp_Old_New_ == "Old") %>%
    mutate(word_acc_filled = ifelse(is.na(word_acc), 0L, word_acc),
           img_acc_filled  = ifelse(is.na(img_acc),  0L, img_acc)) %>%
    group_by(sub) %>%
    summarise(Pre = mean(word_acc_filled == 1 & img_acc_filled == 1) * 100, .groups = "drop"),
  post_raw %>% filter(Corr_resp_Old_New_ == "Old") %>%
    mutate(word_acc_filled = ifelse(is.na(word_acc), 0L, word_acc),
           img_acc_filled  = ifelse(is.na(img_acc),  0L, img_acc)) %>%
    group_by(sub) %>%
    summarise(Post = mean(word_acc_filled == 1 & img_acc_filled == 1) * 100, .groups = "drop"),
  by = "sub")

t_res   <- t.test(acc_wide$Post, acc_wide$Pre, paired = TRUE)
cohen_d <- (mean(acc_wide$Pre) - mean(acc_wide$Post)) / sd(acc_wide$Pre - acc_wide$Post)

cat(sprintf("Pre:  %.1f%% (SD %.1f%%)\n", mean(acc_wide$Pre), sd(acc_wide$Pre)))
cat(sprintf("Post: %.1f%% (SD %.1f%%)\n", mean(acc_wide$Post), sd(acc_wide$Post)))
cat(sprintf("t(%d) = %.2f, p = %.4f, d = %.2f\n",
            t_res$parameter, t_res$statistic, t_res$p.value, cohen_d))
```

---

# 3. Face vs Object Memory

```{r face_object}
both_sess <- bind_rows(
  pre_raw  %>% filter(Corr_resp_Old_New_ == "Old") %>%
               mutate(session = "Pre",  Confidence_Rating = as.character(Confidence_Rating)),
  post_raw %>% filter(Corr_resp_Old_New_ == "Old") %>%
               mutate(session = "Post", Confidence_Rating = as.character(Confidence_Rating))
) %>%
  mutate(
    word_acc_filled = ifelse(is.na(word_acc), 0L, word_acc),
    img_acc_filled  = ifelse(is.na(img_acc),  0L, img_acc),
    correct   = as.integer(word_acc_filled == 1 & img_acc_filled == 1),
    session   = factor(session, levels = c("Pre", "Post")),
    stim_type = factor(Images_Faces_Object_)
  )

m_cat <- glmer(correct ~ stim_type * session + (1 | sub),
               data = both_sess, family = binomial,
               control = glmerControl(optimizer = "bobyqa"))
cat("=== Face vs Object ===\n")
print(Anova(m_cat, type = "II"))

emm_cat <- emmeans(m_cat, ~ stim_type | session, type = "response")
print(emm_cat)
```

```{r diag_m_cat, fig.width=8, fig.height=4}
check_glmm_assumptions(m_cat, "Face vs Object Memory (m_cat)")
```

---

# 4. TMR Efficacy (Cue vs Non-Cue)

```{r tmr_efficacy}
df_tmr <- matched_rec %>%
  filter(Condition_f %in% c("Cue", "Non-Cue")) %>%
  mutate(Condition_f = droplevels(Condition_f))

m_tmr <- glmer(rec_forgetting ~ Condition_f + (1 | sub),
               data = df_tmr, family = binomial,
               control = glmerControl(optimizer = "bobyqa"))

cat("=== TMR Efficacy ===\n")
tmr_anova <- Anova(m_tmr, type = "II")
print(tmr_anova)

emm_tmr  <- emmeans(m_tmr, ~ Condition_f, type = "response")
pair_tmr <- contrast(emm_tmr, method = "pairwise", adjust = "none")
print(summary(pair_tmr))
```

```{r diag_m_tmr, fig.width=8, fig.height=4}
check_glmm_assumptions(m_tmr, "TMR Efficacy (m_tmr)")
```

---

# 5. Familiarity (Word Recognition)

```{r familiarity_glmm}
m_fam <- glmer(fam_forgetting ~ Condition_f + (1 | sub),
               data = matched, family = binomial,
               control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

cat("=== Familiarity GLMM ===\n")
fam_anova <- Anova(m_fam, type = "II")
print(fam_anova)

emm_fam  <- emmeans(m_fam, ~ Condition_f, type = "response")
pair_fam <- contrast(emm_fam, method = "pairwise", adjust = "none")
print(emm_fam)
print(summary(pair_fam))

pair_fam_logit <- contrast(emmeans(m_fam, ~ Condition_f),
                            method = "pairwise", adjust = "none")
print(summary(pair_fam_logit))
```

```{r diag_m_fam, fig.width=8, fig.height=4}
check_glmm_assumptions(m_fam, "Familiarity (m_fam)")
```

```{r fig_familiarity}
emm_fam_df <- as.data.frame(emm_fam) %>%
  mutate(rate_pct = prob * 100, lo_pct = asymp.LCL * 100, hi_pct = asymp.UCL * 100)

pp_familiarity <- matched %>%
  group_by(sub, Condition_f) %>%
  summarise(rate = mean(fam_forgetting, na.rm = TRUE) * 100, .groups = "drop")

sig_fam <- get_sig_pairs_gated(pair_fam, COND_LEVELS,
                               max(pp_familiarity$rate, na.rm = TRUE),
                               fam_anova$`Pr(>Chisq)`[1])

p_familiarity <- ggplot() +
  geom_col(data = emm_fam_df, aes(x = Condition_f, y = rate_pct, fill = Condition_f),
           width = 0.7, colour = NA) +
  geom_errorbar(data = emm_fam_df,
                aes(x = Condition_f, ymin = lo_pct, ymax = hi_pct),
                width = 0.15, linewidth = 0.8, colour = "black") +
  geom_line(data = pp_familiarity,
            aes(x = as.numeric(Condition_f), y = rate, group = sub),
            colour = "grey65", linewidth = 0.45, alpha = 0.65) +
  geom_point(data = pp_familiarity,
             aes(x = Condition_f, y = rate, fill = Condition_f),
             shape = 21, size = 1.4, stroke = 0.5, colour = "black", alpha = 0.85,
             position = position_jitter(width = 0.06, seed = 123, height = 0)) +
  { if (nrow(sig_fam) > 0) list(
      geom_segment(data = sig_fam, aes(x=x1,xend=x2,y=y_bar,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data = sig_fam, aes(x=x1,xend=x1,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data = sig_fam, aes(x=x2,xend=x2,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_text(data=sig_fam, aes(x=(x1+x2)/2,y=y_bar+2,label=sig),
                size=5, inherit.aes=FALSE)
  )} +
  scale_fill_manual(values = COL_COND) +
  scale_y_continuous(labels = percent_format(accuracy=1,scale=1),
                     expand = expansion(mult=c(0,0.2)), limits=c(0,NA)) +
  labs(x = NULL, y = "Word Recognition Forgetting (%)") +
  theme_classic(base_size = 10) +
  theme(legend.position="none",
        axis.line=element_line(linewidth=0.8,colour="black"),
        axis.text.x=element_text(size=10,colour="black",angle=30,hjust=1),
        axis.text.y=element_text(size=10,colour="black"),
        axis.title=element_text(size=10,colour="black"),
        plot.margin=margin(10,10,15,10)) +
  coord_cartesian(clip="off")

print(p_familiarity)
ggsave(file.path(FIG_DIR, "Fig_4_Familiarity.png"), p_familiarity, width=3.2, height=3.2, dpi=600)
ggsave(file.path(FIG_DIR, "Fig_4_Familiarity.pdf"), p_familiarity, width=3.2, height=3.2, device=cairo_pdf)
ggsave(file.path(FIG_DIR, "Fig_4_Familiarity.svg"), p_familiarity, width=3.2, height=3.2, device="svg")
cat("Familiarity figure saved.\n")
```

---

# 6. Recollection (Primary Outcome)

```{r recollection_glmm}
m_rec <- glmer(rec_forgetting ~ Condition_f + (1 | sub),
               data = matched_rec, family = binomial,
               control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

cat("=== Recollection GLMM ===\n")
rec_anova <- Anova(m_rec, type = "II")
print(rec_anova)

emm_rec  <- emmeans(m_rec, ~ Condition_f, type = "response")
pair_rec <- contrast(emm_rec, method = "pairwise", adjust = "none")
print(emm_rec)
print(summary(pair_rec))

pair_rec_logit <- contrast(emmeans(m_rec, ~ Condition_f),
                            method = "pairwise", adjust = "none")
print(summary(pair_rec_logit))

rec_rates <- matched_rec %>%
  group_by(Condition_f) %>%
  summarise(N=n(), Correct_pct=round(mean(rec_correct)*100,1),
            Forgetting_pct=round(mean(rec_forgetting)*100,1),
            SE=round(sd(rec_forgetting)/sqrt(n())*100,1), .groups="drop")
kable(rec_rates, caption="Recollection by condition") %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"))
```

```{r diag_m_rec, fig.width=8, fig.height=4}
check_glmm_assumptions(m_rec, "Recollection - PRIMARY OUTCOME (m_rec)")
```

```{r fig_recollection}
emm_rec_df <- as.data.frame(emm_rec) %>%
  mutate(rate_pct=prob*100, lo_pct=asymp.LCL*100, hi_pct=asymp.UCL*100)

pp_recollection <- matched_rec %>%
  group_by(sub, Condition_f) %>%
  summarise(rate=mean(rec_forgetting,na.rm=TRUE)*100, .groups="drop")

sig_rec <- get_sig_pairs_gated(pair_rec, COND_LEVELS,
                               max(pp_recollection$rate,na.rm=TRUE),
                               rec_anova$`Pr(>Chisq)`[1])

n_sig_rec   <- nrow(sig_rec)
bracket_top <- if (n_sig_rec > 0) max(sig_rec$y_bar) + 3 else max(pp_recollection$rate, na.rm=TRUE) + 5

p_recollection <- ggplot() +
  geom_col(data=emm_rec_df, aes(x=Condition_f,y=rate_pct,fill=Condition_f),
           width=0.7, colour=NA) +
  geom_errorbar(data=emm_rec_df, aes(x=Condition_f,ymin=lo_pct,ymax=hi_pct),
                width=0.15, linewidth=0.8, colour="black") +
  geom_line(data=pp_recollection, aes(x=as.numeric(Condition_f),y=rate,group=sub),
            colour="grey65", linewidth=0.45, alpha=0.65) +
  geom_point(data=pp_recollection, aes(x=Condition_f,y=rate,fill=Condition_f),
             shape=21, size=1.4, stroke=0.5, colour="black", alpha=0.85,
             position=position_jitter(width=0.06,seed=123,height=0)) +
  { if (nrow(sig_rec) > 0) list(
      geom_segment(data=sig_rec, aes(x=x1,xend=x2,y=y_bar,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_rec, aes(x=x1,xend=x1,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_rec, aes(x=x2,xend=x2,y=y_bar-1.5,yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_text(data=sig_rec, aes(x=(x1+x2)/2,y=y_bar+2,label=sig),
                size=5, inherit.aes=FALSE)
  )} +
  scale_fill_manual(values=COL_COND) +
  scale_y_continuous(labels=percent_format(accuracy=1,scale=1),
                     breaks=seq(0,50,10)) +
  coord_cartesian(ylim = c(0, bracket_top), clip = "off") +
  labs(x=NULL, y="Associative Recall Forgetting (%)") +
  theme_classic(base_size=10) +
  theme(legend.position="none",
        axis.line=element_line(linewidth=0.8,colour="black"),
        axis.text.x=element_text(size=10,colour="black",angle=30,hjust=1),
        axis.text.y=element_text(size=10,colour="black"),
        axis.title=element_text(size=10,colour="black"),
        plot.margin=margin(10,10,15,10))

print(p_recollection)
ggsave(file.path(FIG_DIR,"Fig_5_Recollection_Primary.png"), p_recollection, width=3.2, height=3.2, dpi=600)
ggsave(file.path(FIG_DIR,"Fig_5_Recollection_Primary.pdf"), p_recollection, width=3.2, height=3.2, device=cairo_pdf)
ggsave(file.path(FIG_DIR,"Fig_5_Recollection_Primary.svg"), p_recollection, width=3.2, height=3.2, device="svg")
cat("Recollection figure saved.\n")
```

---

# 7. Fidelity Forgetting Index (pre - post score)

```{r fidelity_index}
matched_fid_idx <- matched %>%
  filter(!is.na(pre_scale), pre_scale >= 1, !is.na(post_scale)) %>%
  mutate(fid_forgetting_index = pre_scale - post_scale)

cat("=== Fidelity Forgetting Index (pre - post) ===\n")
matched_fid_idx %>%
  group_by(Condition_f) %>%
  summarise(N    = n(),
            Mean = round(mean(fid_forgetting_index, na.rm = TRUE), 3),
            SD   = round(sd(fid_forgetting_index,   na.rm = TRUE), 3),
            .groups = "drop") %>%
  print()

pp_fid_idx <- matched_fid_idx %>%
  group_by(sub, Condition_f) %>%
  summarise(mean_idx = mean(fid_forgetting_index, na.rm = TRUE), .groups = "drop")

m_fid_idx <- lmer(mean_idx ~ Condition_f + (1 | sub),
                  data = pp_fid_idx)

cat("\n=== Fidelity Index LME — ANOVA (participant level) ===\n")
fid_idx_anova <- anova(m_fid_idx)
print(fid_idx_anova)

emm_idx  <- emmeans(m_fid_idx, ~ Condition_f)
pair_idx <- contrast(emm_idx, method = "pairwise", adjust = "none")
print(emm_idx)
print(summary(pair_idx))
```

```{r diag_m_fid_idx, fig.width=8, fig.height=4}
check_glmm_assumptions(m_fid_idx, "Fidelity Forgetting Index (m_fid_idx, LMM)")
```

```{r fig_fidelity_index}
pp_idx <- matched_fid_idx %>%
  group_by(sub, Condition_f) %>%
  summarise(rate=mean(fid_forgetting_index,na.rm=TRUE), .groups="drop")

sig_idx <- as.data.frame(summary(pair_idx)) %>%
  filter(p.value < .06) %>%
  mutate(
    contrast = as.character(contrast),
    g1  = gsub("[()]", "", trimws(sapply(strsplit(contrast, " - "), `[`, 1))),
    g2  = gsub("[()]", "", trimws(sapply(strsplit(contrast, " - "), `[`, 2))),
    x1  = match(g1, COND_LEVELS),
    x2  = match(g2, COND_LEVELS),
    sig = ifelse(p.value < .001, "***",
                 ifelse(p.value < .01,  "**",
                        ifelse(p.value < .05, "*", "\u2020")))
  ) %>%
  filter(!is.na(x1), !is.na(x2)) %>%
  arrange(abs(x2 - x1)) %>%
  mutate(y_bar = max(pp_idx$rate, na.rm = TRUE) + 0.15 + 0.35 * seq_len(n()))

emm_idx_df <- as.data.frame(emm_idx) %>%
  rename(rate_pct=emmean, lo_pct=lower.CL, hi_pct=upper.CL)

p_fid_idx <- ggplot() +
  geom_col(data=emm_idx_df, aes(x=Condition_f,y=rate_pct,fill=Condition_f),
           width=0.7, colour=NA) +
  geom_errorbar(data=emm_idx_df, aes(x=Condition_f,ymin=lo_pct,ymax=hi_pct),
                width=0.15, linewidth=0.8, colour="black") +
  geom_line(data=pp_idx, aes(x=as.numeric(Condition_f),y=rate,group=sub),
            colour="grey65", linewidth=0.45, alpha=0.65) +
  geom_point(data=pp_idx, aes(x=Condition_f,y=rate,fill=Condition_f),
             shape=21, size=1.4, stroke=0.5, colour="black", alpha=0.85,
             position=position_jitter(width=0.06,seed=123,height=0)) +
  geom_hline(yintercept=0, linetype="dashed", colour="grey40", linewidth=0.4) +
  { if (nrow(sig_idx) > 0) list(
      geom_segment(data=sig_idx,
                   aes(x=x1, xend=x2, y=y_bar, yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_idx,
                   aes(x=x1, xend=x1, y=y_bar-0.10, yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_segment(data=sig_idx,
                   aes(x=x2, xend=x2, y=y_bar-0.10, yend=y_bar),
                   linewidth=0.6, inherit.aes=FALSE),
      geom_text(data=sig_idx,
                aes(x=(x1+x2)/2, y=y_bar+0.10, label=sig),
                size=5, inherit.aes=FALSE)
  )} +
  scale_fill_manual(values=COL_COND) +
  scale_y_continuous(expand=expansion(mult=c(0.1,0.22))) +
  labs(x=NULL, y="Fidelity Forgetting Index\n(pre \u2212 post score)") +
  theme_classic(base_size=10) +
  theme(legend.position="none",
        axis.line=element_line(linewidth=0.8,colour="black"),
        axis.text.x=element_text(size=10,colour="black",angle=30,hjust=1),
        axis.text.y=element_text(size=10,colour="black"),
        axis.title=element_text(size=10,colour="black"),
        plot.margin=margin(10,10,15,10)) +
  coord_cartesian(clip="off")

print(p_fid_idx)
ggsave(file.path(FIG_DIR,"Fig_6d_Fidelity_Index.png"), p_fid_idx, width=3.2, height=3.2, dpi=600)
ggsave(file.path(FIG_DIR,"Fig_6d_Fidelity_Index.pdf"), p_fid_idx, width=3.2, height=3.2, device=cairo_pdf)
ggsave(file.path(FIG_DIR,"Fig_6d_Fidelity_Index.svg"), p_fid_idx, width=3.2, height=3.2, device="svg")
cat("Fidelity index figure saved.\n")
```

---

# 8. Combined Main Figure

Rebuilt to use the Fidelity Forgetting Index panel (Section 7) rather than the
original binary Fidelity panel, since the binary version was removed.

```{r fig_combined_main}
p_main <- (p_recollection | p_familiarity | p_fid_idx) +
  plot_annotation(tag_levels = "A")
print(p_main)
ggsave(file.path(FIG_DIR,"Fig_MAIN_Combined.png"), p_main, width=9.6, height=3.5, dpi=600)
ggsave(file.path(FIG_DIR,"Fig_MAIN_Combined.pdf"), p_main, width=9.6, height=3.5, device=cairo_pdf)
ggsave(file.path(FIG_DIR,"Fig_MAIN_Combined.svg"), p_main, width=9.6, height=3.5, device="svg")
cat("Combined figure saved.\n")
```

---

# 9. Supplementary

## S1. Block-level analysis

```{r supp_block}
pre_block <- pre_raw %>%
  filter(Corr_resp_Old_New_ == "Old") %>%
  mutate(word_acc_filled=ifelse(is.na(word_acc),0L,word_acc),
         img_acc_filled=ifelse(is.na(img_acc),0L,img_acc),
         correct=as.integer(word_acc_filled==1 & img_acc_filled==1),
         block=as.factor(block)) %>%
  filter(!is.na(block))

m_block <- glmer(correct ~ block + (1|sub), data=pre_block, family=binomial,
                 control=glmerControl(optimizer="bobyqa"))
cat("=== Block ===\n"); print(Anova(m_block, type="II"))
```

```{r diag_m_block, fig.width=8, fig.height=4}
check_glmm_assumptions(m_block, "Pre-nap block-level accuracy (m_block)")
```

---

# 10. Export Tables

```{r export}
writexl::write_xlsx(
  list(
    Familiarity_rates  = matched %>%
      group_by(Condition_f) %>%
      summarise(N=n(), Correct_pct=round(mean(fam_correct)*100,1),
                Forgetting_pct=round(mean(fam_forgetting)*100,1),
                SE=round(sd(fam_forgetting)/sqrt(n())*100,1), .groups="drop"),
    Recollection_rates = rec_rates,
    Fam_pairwise_OR    = as.data.frame(summary(pair_fam)),
    Fam_pairwise_zp    = as.data.frame(summary(pair_fam_logit)),
    Rec_pairwise_OR    = as.data.frame(summary(pair_rec)),
    Rec_pairwise_zp    = as.data.frame(summary(pair_rec_logit)),
    Fid_Index_pairwise = as.data.frame(summary(pair_idx)),
    TMR_pairwise       = as.data.frame(summary(pair_tmr)),
    PrePost_accuracy   = acc_wide
  ),
  path = file.path(TABLE_DIR, "MYSTI_Behavioural_Statistical_Results.xlsx")
)
cat(sprintf("Tables saved to: %s\n", TABLE_DIR))
```

---

# 11. Results Summary

```{r summary}
cat("══════════════════════════════════════════════════════════\n")
cat("RESULTS SUMMARY — BEHAVIOURAL ANALYSIS\n")
cat("══════════════════════════════════════════════════════════\n\n")

cat(sprintf("Overall pre vs post: t(%d) = %.2f, p = %.4f, d = %.2f\n\n",
            t_res$parameter, t_res$statistic, t_res$p.value, cohen_d))
cat(sprintf("TMR efficacy: chi2(%d) = %.2f, p = %.4f\n\n",
            tmr_anova$Df, tmr_anova$Chisq, tmr_anova$`Pr(>Chisq)`))
cat(sprintf("Familiarity: chi2(%d) = %.2f, p = %.4f\n\n",
            fam_anova$Df, fam_anova$Chisq, fam_anova$`Pr(>Chisq)`))
cat(sprintf("Recollection: chi2(%d) = %.2f, p = %.4f\n\n",
            rec_anova$Df, rec_anova$Chisq, rec_anova$`Pr(>Chisq)`))
cat(sprintf("Fidelity Forgetting Index: F(%s) = %.2f, p = %.4f\n\n",
            paste(fid_idx_anova$NumDF, fid_idx_anova$DenDF, sep=","),
            fid_idx_anova$`F value`, fid_idx_anova$`Pr(>F)`))
cat("══════════════════════════════════════════════════════════\n")
```

---

# 12. Session Information

```{r session_info}
sessionInfo()
```
